### 2016-08-01 eda/sentiment-analysis.Rmd
sentiment-analysis

---
title: "sentiment-analysis"
author: "Anuj Desai"
date: "August 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(tm)
```

## Sentiment Analysis on Text Reviews for Yelp

Sentiment analysis, or opinion mining, makes use of natural language processing to analyze pieces of text and determine the attitude of the speaker or writer. In order to find relevant lexicons to explore this topic with the Yelp review data, I researched different lexicons and found ANEW (Affective Norms for English Words), a "sentiment lexcion" that scores words for valence.

However, upon further research, I came across an article written by Finn ˚Arup Nielsen, where he compares a sentiment lexicon he created to ANEW. His list, AFINN, contains a list of English words and assigns an integer from -5 (negative) to +5 (positive) to each word based on its sentiment. He concluded that his word list better classifies sentiment rating than ANEW on Twitter sentiment analysis. Since Yelp ratings are similar to tweets, I'll use AFINN for this exploration.

To see the full study, check out the paper found here: http://www2.imm.dtu.dk/pubdb/views/edoc_download.php/6006/pdf/imm6006.pdf.

Now to apply this sentiment analysis to the Yelp review dataset, I have to mutate the data so that each word for every review exists in one row. I also need to remove stop words like "the", "and", "I", etc. since they don't indicate anything about the attitude of the reviewer and shouldn't affect the valence score. A library called __tm__ for text mining can eliminate stop words. 
```{r, eval = F}
review_words <- reviews %>% 
  mutate(words = str_split(text, "[ ,.]")) %>% 
  unnest(words)

# create corpus for tm
corpus <- Corpus(VectorSource(review_words$words))
# Convert to lower-case
corpus <- tm_map(corpus, tolower)
# remove stop_words
corpus <- tm_map(corpus, function(x) removeWords(x,stopwords()))

head(review_words, n = 5)
```

Too slow. I'll try the library __tidytext__. This library also let's me generate valence scores using the AFINN library without having to write an unnecessarily long function.

```{r, eval = F}
# unnest_tokens splits column into tokens using tokenizers package
# splits "text" column into individual words to analyze sentiment for further
# exploration
reviews_text <- reviews %>% 
  select(business_id, review_id, stars, text) %>%
  unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>% 
  arrange(review_id)

# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
# sentiments: 
#   data frame with 4 variables: word, sentiment, lexicon, score
# lexicon can be "nrc", "bing", or "AFINN"
word_affinity <- sentiments %>% 
  filter(lexicon == "AFINN") %>% 
  select(word, score)

# calculate mean for each group of stars
review_scores <- reviews_text %>% 
  inner_join(word_affinity, by = "word") %>% 
  group_by(review_id, stars) %>% 
  summarise(sentiment = mean(score))
```

### 2016-08-02 eda/sentiment-analysis.Rmd
reworked bug

@@
 ```
+
+Pretty fast. I'll stick to this library and generate five box-plots to see if there's a positive correlation between mean sentiment score and restaurant rating.
+
+```{r, eval = F}
+# boxplot for each group
+ggplot(reviews_scores) +
+  geom_boxplot(aes(stars, sentiment, group = stars)) +
+  labs(x = "Business Rating",
+       y = "Mean Sentiment Score",
+       title = "Mean Sentiment Score vs. Business Rating")
+
+one <- reviews_text %>% 
+  filter(stars == 1) %>% 
+  group_by(word) %>% 
+  count() %>% 
+  top_n(200) %>% 
+  arrange(n)
+
+wordcloud::wordcloud(one$word, one$n, scale = c(5, 0.5),
+                     random.order = F, random.color = F,
+                     use.r.layout = T,
+                     colors = RColorBrewer::brewer.pal(10, "Reds"))
+```

### 2016-08-02 eda/sentiment-analysis.Rmd
ggplot sentiments

--- 2016-08-01 eda/sentiment-analysis.Rmd
@@
 # lexicon can be "nrc", "bing", or "AFINN"
-word_affinity <- sentiments %>% 
+valence_score <- sentiments %>% 
   filter(lexicon == "AFINN") %>% 
@@
 review_scores <- reviews_text %>% 
-  inner_join(word_affinity, by = "word") %>% 
+  inner_join(valence_score, by = "word") %>% 
   group_by(review_id, stars) %>% 
@@
 ```
+
+Pretty fast. I'll stick to this library and generate five box-plots to see if there's a positive correlation between mean sentiment score and restaurant rating.
+
+```{r, eval = F}
+# boxplot for each group
+ggplot(review_scores) +
+  geom_boxplot(aes(stars, sentiment, group = stars)) +
+  labs(x = "Business Star Rating",
+       y = "Mean Sentiment Score",
+       title = "Mean Sentiment Score vs. Business Star Rating") +
+  theme_bw()
+```

### 2016-08-02 eda/word-cloud.Rmd
wordclouds one/five-star

---
title: "word-cloud"
author: "Anuj Desai"
date: "August 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(wordcloud)
library(readr)
library(dplyr)
library(tidyr)
```

## Word Clouds
```{r}
reviews_text <- read_csv("../clean_data/reviews_text.csv")
one <- reviews_text %>% 
  filter(stars == 1) %>% 
  group_by(word) %>% 
  count() %>% 
  top_n(100) %>% 
  arrange(n)
five <- reviews_text %>% 
  filter(stars == 5) %>% 
  group_by(word) %>% 
  count() %>% 
  top_n(100) %>% 
  arrange(n)

col <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
wordcloud(one$word, one$n, scale = c(4, 0.25),
          random.order = F, random.color = F,
          use.r.layout = T, rot.per = .35,
          colors = col)
green <- c("palegreen", "springgreen2", "mediumseagreen", "forestgreen", "darkgreen")
wordcloud(five$word, five$n, scale = c(4, 0.25),
          random.order = F, random.color = F,
          use.r.layout = T, rot.per = .35,
          colors = green)
```

### 2016-08-02 eda/word-cloud.Rmd
word-clouds

@@
 ## Word Clouds
+
+Created some word clouds for one-star and five-star businesses to see if there's a difference between the words reviewers use for each rating using __wordcloud__ library.
+Expect to see a relationship between negative words and one-star ratings and positive words and five-star ratings.
 ```{r}
@@
   arrange(n)
+
 five <- reviews_text %>% 
@@
           colors = col)
-green <- c("palegreen", "springgreen2", "mediumseagreen", "forestgreen", "darkgreen")
+green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
+           "seagreen", "darkgreen")
 wordcloud(five$word, five$n, scale = c(4, 0.25),
@@
 ```
+
+The main words are similar for both clouds like "food" and "service", probably because it was bad food and service for one-star restaurants and great food and service for five-star restaurants.
+Evidence of this is present in the other words like "love", "friendly", "excellent", "happy" for five-stars and "bad", "rude", "worst", "wait", "horrible" for one-stars.

### 2016-08-03 eda/business-attributes.Rmd
business attribute data cleaning process added

---
title: "business-attributes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(maps)
library(jsonlite)
```

## Where most reviews are clustered in US

Among 70k+ businesses registered on Yelp, I wanted to figure out more about what makes a business successful. Before investigating deeper, I decided to look at businesses that has 300+ reviews on Yelp by users in order to get more objective ratings of the business. I filtered the data set to get rid of closed businesses, businesses outside of US and limited the business type to restaurants.

```{r}
us_business <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/us-business.csv', stringsAsFactors=FALSE)
noise_level <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
attire_type <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

## Exploring Noise Level

As expected, restaurants with many reviews and/or high ratings were clustered in specific regions. This table shows where most restaurants are clustered around. I have chosen 4 regions with most businesses: Nevada, Arizona, North Carolina and Pennsylvania.

```{r}
top_data <- us_business %>% 
  group_by(state) %>% 
  tally()
top_data
```

There were many attributes per restaurant, and some were more influential directly/indirectly to a business' success. I have first decided to see how noise level would influcence the star ratings of customers. 
I grouped the data frame by 'state' and 'noise' and created a new column having the average star rating per group. The plot didn't know which noise level to plot first, so I have created the factor levels in noise level.

```{r}
ggplot(data=noise_level, aes(x = noise_factored,
                            y = star, 
                            fill = state)) +
  geom_bar(stat = "identity", 
           position = "dodge") +
  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
  labs(title = "How Noise Level Influences Average Star Ratings") + 
  xlab("Noise Level") + 
  ylab("Average Star Ratings") +
  guides(fill = guide_legend("Region"))
```

## Exploring Attire Types
Now to another business attribute: attire. Similar to noise data, attire_data was retrived by grouping the data frame by 'state' and 'attire'. Again, the star ratings were the means of each group's star ratings.

```{r}
ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
  geom_bar(stat="identity", position = "dodge") +
  labs(title = "How Attire Influences Average Star Ratings") + 
  xlab("Attire") + 
  ylab("Average Star Ratings") + 
  guides(fill = guide_legend("Region"))
```

### 2016-08-03 business.R

@@ -5,6 +5,7 @@ library(tidyr)
 library(magrittr)
 library(ggmap)
 library(maps)
+library(jsonlite)
 
 business <- fromJSON(sprintf("[%s]", 
                              paste(readLines("yelp_academic_dataset_business.json"), 
@@ -16,7 +17,7 @@ business <- fromJSON(sprintf("[%s]",
 names(business) <- c("open", "categories", "count", "long", "lat", "state", "stars", "noise", "attire")
 states <- map_data('state')
 # Show data from all over US
-us_business <- filter(business, review_count > 300)
+us_business <- filter(business, count > 300)
 ggplot(states) + 
   geom_polygon(aes(x = long, 
                    y = lat, 
@@ -25,11 +26,15 @@ ggplot(states) +
                color = "white") + 
   coord_fixed(1.3) + 
   geom_point(data = us_business, 
-             aes(longitude, 
-                 latitude, 
-                 color = stars, 
-                 size = review_count), 
-             alpha = 0.5)
+             aes(long, 
+                 lat, 
+                 color = factor(stars), 
+                 size = count), 
+             alpha = 0.7) + 
+  guides(colour = guide_legend("Star Rating"), 
+         size = guide_legend("Review Counts")) + 
+  labs(title = "Restaurant Reviews in United States") +
+  theme_nothing(legend = TRUE)
 # Show number of businesses in each state (popularity) 
 top_data <- us_business %>% 
   group_by(state) %>% 
@@ -38,17 +43,31 @@ top_data <- us_business %>%
 # Focusing on attribute noise level
 noise_data <- business %>% 
   na.omit() %>% 
-  filter(state == "NV" | state == "AZ") %>% 
+  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
   group_by(state, noise) %>% 
-  summarise(star = mean(stars))
-ggplot(data=noise_data, aes(x=noise, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") 
+  summarise(star = mean(stars)) 
+noise_data$noise_factored <- factor(noise_data$noise, 
+                                labels=c("quiet",
+                                         "average",
+                                         "loud", 
+                                         "very_loud"))  
+ggplot(data=noise_data, aes(x=noise_factored, y=star, fill=state)) +
[…]

### 2016-08-03 clean_data/CleanData.R

@@ -1,0 +1,35 @@
+business <- fromJSON(sprintf("[%s]", 
+                             paste(readLines("yelp_academic_dataset_business.json"), 
+                                   collapse = ","))) %>% 
+  flatten() %>% 
+  select(open, categories, review_count, longitude, latitude, state, stars, latitude, `attributes.Noise Level`, `attributes.Attire`) %>% 
+  # should filter for restaurants 
+  filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
+names(business) <- c("open", "categories", "count", "long", "lat", "state", "stars", "noise", "attire")
+
+# Business data with review counts exceeding 300.
+us_business <- filter(business, count > 300) 
+us_business <- data.frame(lapply(us_business, as.character), 
+                          stringsAsFactors=FALSE)
+write.csv(subset(us_business), "us-business.csv")
+
+# Data: Star ratings with noise level attribute
+noise_level <- business %>% 
+  na.omit() %>% 
+  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
+  group_by(state, noise) %>% 
+  summarise(star = mean(stars)) 
+noise_level$noise_factored <- factor(noise_level$noise, 
+                                    labels=c("quiet",
+                                             "average",
+                                             "loud", 
+                                             "very_loud"))  
+write.csv(subset(noise_level), "noise-attr.csv")
+
+# Data: Star ratings with attire type attribute
+attire_type <- business %>% 
+  na.omit() %>% 
+  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
+  group_by(state, attire) %>% 
+  summarise(star = mean(stars))
+write.csv(subset(attire_type), "attire-attr.csv")

### 2016-08-03 location.R

@@ -1,0 +1,61 @@
+library(readr)
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(magrittr)
+library(ggmap)
+library(maps)
+library(jsonlite)
+
+review <- fromJSON(sprintf("[%s]", 
+                           paste(read_lines("yelp_academic_dataset_review.json", 
+                                            n_max = 1500000), 
+                                 collapse = ","))) %>% 
+  select(user_id, review_id, stars, business_id)
+
+
+user <- fromJSON(sprintf("[%s]", 
+                         paste(read_lines("yelp_academic_dataset_user.json",
+                                          n_max = 100000), 
+                               collapse = ",")))
+
+business_location <- fromJSON(sprintf("[%s]", 
+                             paste(readLines("yelp_academic_dataset_business.json"), 
+                                   collapse = ","))) %>% 
+  select(business_id, city)
+
+user <- user[order(-user$review_count),] %>% 
+  head(15) %>% 
+  select(name, user_id, review_count)
+
+# Join user and review by user_id
+user_reviews <- left_join(user, review) %>% 
+  left_join(business_location) 
+  
+u <- group_by(user_reviews, user_id, city) %>% 
+  tally()
+
+max_reviews <- aggregate(n ~ user_id, u, max) %>% 
+  left_join(u) %>% 
+  select(-n) %>% 
+  mutate(max_review=TRUE)
+
+user_reviews <- left_join(user_reviews, max_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+user_reviews <- user_reviews %>% 
+  group_by(name, max_review) %>% 
+  summarise(val = mean(stars)) %>% 
+  mutate(count = n()) %>% 
+  filter(count == 2)
+
+ggplot(user_reviews, aes(x = max_review,
+                         y = val)) +
+  geom_bar(stat = "identity", 
+           position = "dodge") + 
+  facet_wrap(~name) + 
+  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
+  xlab("Location") + 
+  ylab("Star Ratings") +
+  scale_x_discrete(labels=c("Travelling", "Home"))
+  scale_x_discrete(labels=c("Travelling", "Home"))

### 2016-08-03 eda/sentiment-analysis.Rmd
rscripts for cleaning

@@
 A library called __tm__ for text mining can eliminate stop words.
+I'll read in the first 500,000 observations of the Yelp reviewers data, which has been written to a csv file.
 ```{r, eval = F}
+reviews <- read_csv("clean_data/reviews.csv")
+
 review_words <- reviews %>% 
@@
 ```
+
+Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
+
+```{r}
+review_words <- reviews_text %>% 
+  count(review_id, business_id, stars, word) %>% 
+  ungroup() %>% 
+  group_by(business = n_distinct(business_id),
+           reviews = n(),
+           use = sum(n),
+           average_star = mean(stars)) %>% 
+  ungroup()
+```

### 2016-08-03 business.R

@@ -1,54 +1,0 @@
-library(readr)
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(magrittr)
-library(ggmap)
-library(maps)
-
-business <- fromJSON(sprintf("[%s]", 
-                             paste(readLines("yelp_academic_dataset_business.json"), 
-                                   collapse = ","))) %>% 
-  flatten() %>% 
-  select(open, categories, review_count, longitude, latitude, state, stars, latitude, `attributes.Noise Level`, `attributes.Attire`) %>% 
-  # should filter for restaurants 
-  filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
-names(business) <- c("open", "categories", "count", "long", "lat", "state", "stars", "noise", "attire")
-states <- map_data('state')
-# Show data from all over US
-us_business <- filter(business, review_count > 300)
-ggplot(states) + 
-  geom_polygon(aes(x = long, 
-                   y = lat, 
-                   group = group), 
-               fill = "grey80", 
-               color = "white") + 
-  coord_fixed(1.3) + 
-  geom_point(data = us_business, 
-             aes(longitude, 
-                 latitude, 
-                 color = stars, 
-                 size = review_count), 
-             alpha = 0.5)
-# Show number of businesses in each state (popularity) 
-top_data <- us_business %>% 
-  group_by(state) %>% 
-  tally()
-
-# Focusing on attribute noise level
-noise_data <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ") %>% 
-  group_by(state, noise) %>% 
-  summarise(star = mean(stars))
-ggplot(data=noise_data, aes(x=noise, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") 
-
-# Focusing on attribute attire
-attire_data <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ") %>% 
-  group_by(state, attire) %>% 
-  summarise(star = mean(stars))
-ggplot(data=attire_data, aes(x=attire, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") 

### 2016-08-03 rscripts/sentiments.R

@@ -1,0 +1,52 @@
+library(jsonlite)
+library(readr)
+library(httr)
+library(stringr)
+library(tidytext)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+library(tm)
+# users <- fromJSON(sprintf("[%s]", 
+#                             paste(readLines("data/yelp_academic_dataset_user.json"), 
+#                                   collapse = ",")))
+reviews <- fromJSON(sprintf("[%s]", 
+                    paste(read_lines("data/yelp_academic_dataset_review.json", 
+                                     n_max = 500000), 
+                    collapse = ","))) %>% 
+  flatten() %>% 
+  tbl_df()
+
+# unnest_tokens splits column into tokens using tokenizers package
+# splits "text" column into individual words to analyze sentiment for further
+# exploration
+reviews_text <- reviews %>% 
+  select(business_id, review_id, stars, text) %>%
+  unnest_tokens(word, text) %>% 
+  anti_join(stop_words) %>% 
+  arrange(review_id)
+
+# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
+# sentiments: 
+#   data frame with 4 variables: word, sentiment, lexicon, score
+# lexicon can be "nrc", "bing", or "AFINN"
+valence_score <- sentiments %>% 
+  filter(lexicon == "AFINN") %>% 
+  select(word, score)
+
+# calculate mean for each group of stars
+review_scores <- reviews_text %>% 
+  inner_join(valence_score, by = "word") %>% 
+  group_by(review_id, stars) %>% 
+  summarise(sentiment = mean(score))
+
+write_csv(reviews_text, "data/reviews_text.csv")
+write_csv(valence_score, "data/valence_score.csv")
+
+ggplot(review_scores) +
+  geom_boxplot(aes(stars, sentiment, group = stars)) +
+  labs(x = "Business Rating",
+       y = "Average Sentiment Score",
+       title = "Average Sentiment Score vs. Business Rating")
+  

### 2016-08-03 eda/business-attributes.Rmd
location data explanation added

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r packages, include = FALSE}
 library(readr)
+library(stringr)
 library(ggplot2)
@@
 ```{r}
-us_business <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/us-business.csv', stringsAsFactors=FALSE)
-noise_level <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
-attire_type <- read.csv('/Users/irenelee/Desktop/SUMMER16/stat133/final_project/clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
+us_business <- read_csv('../clean_data/us-business.csv', stringsAsFactors=FALSE)
+noise_level <- read_csv('../clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
+attire_type <- read_csv('../clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
 states <- map_data('state')

### 2016-08-03 eda/location-ratings.Rmd
location data explanation added

---
title: "location-ratings"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(maps)
library(jsonlite)
```

## User Reviews Are Influenced While Traveling

I wanted to see if YELP users' review ratings change when they are traveling. This required 3 different data sets: business data, reviews data and user data. In order to select samples that can represent user trends, 15 users that have most number of reviews were selected. By selecting columns that I need for plots,  three different data tables are joined. After grouping by 'user' one location where users are most familiar with is selected and I decided to compare this location to all the other locations. I have ignored data table rows that have  same number of reviews for all cities.

```{r}
user_reviews <- read_csv("user-reviews.csv")
ggplot(user_reviews, aes(x = max_review,
                         y = val)) +
  geom_bar(stat = "identity", 
           position = "dodge") + 
  facet_wrap(~name) + 
  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
  xlab("Location") + 
  ylab("Star Ratings") +
  scale_x_discrete(labels=c("Travelling", "Home"))
  scale_x_discrete(labels=c("Travelling", "Home"))
```

## Plot

Using 'facet_wrap', I was able to plot 11 different bar graphs per user. The second bar graph represents mean star rating for one city that the user wrote most reviews in. The first bar graph represents every other city the user has reviewed.

### 2016-08-03 clean_data/CleanData.R

@@ -33,3 +33,48 @@ attire_type <- business %>%
   group_by(state, attire) %>% 
   summarise(star = mean(stars))
 write.csv(subset(attire_type), "attire-attr.csv")
+
+# Data: 
+review <- fromJSON(sprintf("[%s]", 
+                           paste(read_lines("yelp_academic_dataset_review.json", 
+                                            n_max = 1500000), 
+                                 collapse = ","))) %>% 
+  select(user_id, review_id, stars, business_id)
+
+
+user <- fromJSON(sprintf("[%s]", 
+                         paste(read_lines("yelp_academic_dataset_user.json",
+                                          n_max = 100000), 
+                               collapse = ",")))
+
+business_location <- fromJSON(sprintf("[%s]", 
+                                      paste(readLines("yelp_academic_dataset_business.json"), 
+                                            collapse = ","))) %>% 
+  select(business_id, city)
+
+user <- user[order(-user$review_count),] %>% 
+  head(15) %>% 
+  select(name, user_id, review_count)
+
+# Join user and review by user_id
+user_reviews <- left_join(user, review) %>% 
+  left_join(business_location) 
+
+u <- group_by(user_reviews, user_id, city) %>% 
+  tally()
+
+max_reviews <- aggregate(n ~ user_id, u, max) %>% 
+  left_join(u) %>% 
+  select(-n) %>% 
+  mutate(max_review=TRUE)
+
+user_reviews <- left_join(user_reviews, max_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+user_reviews <- user_reviews %>% 
+  group_by(name, max_review) %>% 
+  summarise(val = mean(stars)) %>% 
+  mutate(count = n()) %>% 
+  filter(count == 2)
+
+write.csv(subset(user_reviews), "user-reviews.csv")

### 2016-08-03 location.R

@@ -4,6 +4,7 @@ library(dplyr)
 library(tidyr)
 library(magrittr)
 library(ggmap)
+
 library(maps)
 library(jsonlite)
 

### 2016-08-03 eda/business-attributes.Rmd
cleaning data

@@
 ```{r}
-us_business <- read_csv('../clean_data/us-business.csv', stringsAsFactors=FALSE)
-noise_level <- read_csv('../clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
-attire_type <- read_csv('../clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
+us_business <- read_csv('../clean_data/us-business.csv')
+noise_level <- read_csv('../clean_data/noise-attr.csv')
+attire_type <- read_csv('../clean_data/attire-attr.csv')
 states <- map_data('state')

### 2016-08-03 eda/word-cloud.Rmd
cleaning data

@@
 library(tidyr)
+source("../functions/wordcloud.R")
 ```
@@
 
-col <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
-wordcloud(one$word, one$n, scale = c(4, 0.25),
-          random.order = F, random.color = F,
-          use.r.layout = T, rot.per = .35,
-          colors = col)
+red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
+word_cloud(one$word, one$n, red)
 green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
            "seagreen", "darkgreen")
-wordcloud(five$word, five$n, scale = c(4, 0.25),
-          random.order = F, random.color = F,
-          use.r.layout = T, rot.per = .35,
-          colors = green)
+word_cloud(five$word, five$n, green)
 ```

### 2016-08-03 eda/business-attributes.Rmd
updates in attributes

@@
 ```{r}
-us_business <- read_csv('../clean_data/us-business.csv')
-noise_level <- read_csv('../clean_data/noise-attr.csv')
-attire_type <- read_csv('../clean_data/attire-attr.csv')
+us_business <- read_csv('us-business.csv')
+noise_level <- read_csv('noise-attr.csv') 
+attire_type <- read_csv('attire-attr.csv')
 states <- map_data('state')

### 2016-08-03 eda/location-ratings.Rmd
updates in attributes

@@
 ```{r}
-user_reviews <- read_csv("user-reviews.csv")
+user_reviews <- read_csv("../clean_data/user-reviews.csv")
 ggplot(user_reviews, aes(x = max_review,

### 2016-08-03 rscripts/business.R

@@ -11,7 +11,7 @@ business <- fromJSON(sprintf("[%s]",
                              paste(readLines("yelp_academic_dataset_business.json"), 
                                    collapse = ","))) %>% 
   flatten() %>% 
-  select(open, categories, review_count, longitude, latitude, state, stars, latitude, `attributes.Noise Level`, `attributes.Attire`) %>% 
+  select(open, categories, review_count, state, stars, `attributes.Noise Level`, `attributes.Attire`, `attributes.Take-out`, `attributes.Takes Reservations` `attributes.Delivery`, `attributes.Outdoor Seating`, `attributes.Accepts Credit Cards`,`attributes.Happy Hour`) %>% 
   # should filter for restaurants 
   filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
 names(business) <- c("open", "categories", "count", "long", "lat", "state", "stars", "noise", "attire")
@@ -40,10 +40,11 @@ top_data <- us_business %>%
   group_by(state) %>% 
   tally()
 
-# Focusing on attribute noise level
-noise_data <- business %>% 
+big_cities <- business %>% 
   na.omit() %>% 
-  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
+  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA")
+# Focusing on attribute noise level
+noise_data <- big_cities %>% 
   group_by(state, noise) %>% 
   summarise(star = mean(stars)) 
 noise_data$noise_factored <- factor(noise_data$noise, 
@@ -60,9 +61,7 @@ ggplot(data=noise_data, aes(x=noise_factored, y=star, fill=state)) +
   guides(fill = guide_legend("Region"))
 
 # Focusing on attribute attire
-attire_data <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
+attire_data <- big_cities %>% 
   group_by(state, attire) %>% 
   summarise(star = mean(stars))
 ggplot(data=attire_data, aes(x=attire, y=star, fill=state)) +
@@ -71,3 +70,4 @@ ggplot(data=attire_data, aes(x=attire, y=star, fill=state)) +
   xlab("Attire") + 
   ylab("Average Star Ratings") + 
   guides(fill = guide_legend("Region"))
+

### 2016-08-03 eda/sentiment-analysis.Rmd
cleaning data

--- 2016-08-02 eda/sentiment-analysis.Rmd
@@
 library(dplyr)
-library(tidytext)
 library(tm)
@@
 
+I'll read in the first 500,000 observations of the Yelp reviewers data, which has been written to a csv file.
+```{r}
+reviews <- read_csv("../clean_data/reviews.csv")
+```
+
 Now to apply this sentiment analysis to the Yelp review dataset, I have to mutate the data so that each word for every review exists in one row.
@@
 A library called __tm__ for text mining can eliminate stop words.
+
 ```{r, eval = F}
@@
 
-```{r, eval = F}
-# unnest_tokens splits column into tokens using tokenizers package
-# splits "text" column into individual words to analyze sentiment for further
-# exploration
-reviews_text <- reviews %>% 
-  select(business_id, review_id, stars, text) %>%
-  unnest_tokens(word, text) %>% 
-  anti_join(stop_words) %>% 
-  arrange(review_id)
-
-# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
-# sentiments: 
-#   data frame with 4 variables: word, sentiment, lexicon, score
-# lexicon can be "nrc", "bing", or "AFINN"
-valence_score <- sentiments %>% 
-  filter(lexicon == "AFINN") %>% 
-  select(word, score)
-
-# calculate mean for each group of stars
-review_scores <- reviews_text %>% 
-  inner_join(valence_score, by = "word") %>% 
-  group_by(review_id, stars) %>% 
-  summarise(sentiment = mean(score))
+```{r, eval = T}
+# moved all tidy procedures to CleanData.R
+review_scores <- read_csv("../clean_data/review_scores.csv")
 ```
@@
 
-```{r, eval = F}
+```{r, eval = T}
 # boxplot for each group
@@
 ```
+
+Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
+
+```{r fig.width = 8}
+summaries <- read_csv("../clean_data/summaries.csv")
+
+summaries %>% 
+  ggplot(aes(reviews, average_star, color = score)) +
+  geom_point() +
+  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
+  scale_x_log10() +
+  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
+  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
+  labs(x = "# of reviews",
+       y = "Average Stars",
+       color = "AFINN") +
+  theme_bw()
+```

### 2016-08-03 clean_data/CleanData.R

@@ -7,20 +7,20 @@ library(stringr)
 
 # Read in raw data
 business <- fromJSON(sprintf("[%s]", 
-                     paste(read_lines("../rawdata/yelp_academic_dataset_business.json"), 
+                     paste(read_lines("../raw_data/yelp_academic_dataset_business.json"), 
                      collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
 
 reviews <- fromJSON(sprintf("[%s]", 
-                    paste(read_lines("../rawdata/yelp_academic_dataset_business.json", 
+                    paste(read_lines("../raw_data/yelp_academic_dataset_review.json", 
                                      n_max = 500000), 
                     collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
 
 users <- fromJSON(sprintf("[%s]", 
-                  paste(read_lines("../rawdata/yelp_academic_dataset_users.json"), 
+                  paste(read_lines("../raw_data/yelp_academic_dataset_user.json"), 
                   collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
@@ -70,4 +70,4 @@ summaries <- review_words %>%
 
 # WRITE ALL CSV FILES HERE
 write_csv(review_scores, "review_scores.csv")
-write_csv(review_words, "review_words.csv")
+write_csv(summaries, "summaries.csv")

### 2016-08-04 eda/sentiment-analysis.Rmd
fixed clean_data

@@
 library(dplyr)
+library(tidytext)
 library(tm)
@@
 ```{r, eval = T}
-# moved all tidy procedures to CleanData.R
-review_scores <- read_csv("../clean_data/review_scores.csv")
+# unnest_tokens splits column into tokens using tokenizers package
+# splits "text" column into individual words to analyze sentiment for further
+# exploration
+reviews_text <- reviews %>% 
+  select(business_id, review_id, stars, text) %>%
+  unnest_tokens(word, text) %>% 
+  anti_join(stop_words) %>% 
+  arrange(review_id)
+
+# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
+# sentiments: 
+#   data frame with 4 variables: word, sentiment, lexicon, score
+# lexicon can be "nrc", "bing", or "AFINN"
+valence_score <- sentiments %>% 
+  filter(lexicon == "AFINN") %>% 
+  select(word, score)
+
+# calculate mean for each group of stars
+# Tidied csv: review_id, star rating, average sentiment score
+review_scores <- reviews_text %>% 
+  inner_join(valence_score, by = "word") %>% 
+  group_by(review_id, stars) %>% 
+  summarise(sentiment = mean(score))
 ```
@@
 Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
+```{r}
+# create summary of words and their average sentiment score in each unique
+# review and filter for >= 500 reviews and >= 10 businesses
+# Tidied csv: word, # of businesses word appears, # of reviews word appears,
+# # of different uses of word, average stars of word
+review_words <- reviews_text %>% 
+  count(review_id, business_id, stars, word) %>% 
+  ungroup()
+summaries <- review_words %>% 
+  group_by(word) %>% 
+  summarise(business = n_distinct(business_id),
+            reviews = n(),
+            use = sum(n),
+            average_star = mean(stars)) %>% 
+  ungroup() %>% 
+  filter(reviews >= 500, business >= 10) %>% 
+  inner_join(valence_score, by = "word")
+head(summaries, n = 10)
+```
 
-```{r fig.width = 8}
-summaries <- read_csv("../clean_data/summaries.csv")
-
+```{r fig.height = 7, fig.width = 7}
 summaries %>% 
@@
   geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
-  scale_x_log10() +
+  scale_x_log10(limits = c(200, 100000), 
+                breaks = c(1000, 10000), labels = c(1000, 10000)) +
   geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +

### 2016-08-04 clean_data/CleanData.R

@@ -1,73 +1,30 @@
 library(jsonlite)
 library(dplyr)
-library(tidyr)
 library(readr)
-library(tidytext)
-library(stringr)
 
-# Read in raw data
+# Read in raw data convert to data frames
 business <- fromJSON(sprintf("[%s]", 
-                     paste(read_lines("../raw_data/yelp_academic_dataset_business.json"), 
+                     paste(read_lines(
+                       "../raw_data/yelp_academic_dataset_business.json"), 
                      collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
 
 reviews <- fromJSON(sprintf("[%s]", 
-                    paste(read_lines("../raw_data/yelp_academic_dataset_review.json", 
-                                     n_max = 500000), 
+                    paste(read_lines(
+                      "../raw_data/yelp_academic_dataset_review.json"), 
                     collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
 
 users <- fromJSON(sprintf("[%s]", 
-                  paste(read_lines("../raw_data/yelp_academic_dataset_user.json"), 
+                  paste(read_lines(
+                    "../raw_data/yelp_academic_dataset_user.json"), 
                   collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
 
-## Sentiment Analysis tidying
-
-# unnest_tokens splits column into tokens using tokenizers package
-# splits "text" column into individual words to analyze sentiment for further
-# exploration
-reviews_text <- reviews %>% 
-  select(business_id, review_id, stars, text) %>%
-  unnest_tokens(word, text) %>% 
-  anti_join(stop_words) %>% 
-  arrange(review_id)
-
-# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
-# sentiments: 
-#   data frame with 4 variables: word, sentiment, lexicon, score
-# lexicon can be "nrc", "bing", or "AFINN"
-valence_score <- sentiments %>% 
-  filter(lexicon == "AFINN") %>% 
-  select(word, score)
-
-# calculate mean for each group of stars
-# Tidied csv: review_id, star rating, average sentiment score
-review_scores <- reviews_text %>% 
-  inner_join(valence_score, by = "word") %>% 
-  group_by(review_id, stars) %>% 
-  summarise(sentiment = mean(score))
-
-# create summary of words and their average sentiment score in each unique
[…]

### 2016-08-04 eda/sentiment-analysis.Rmd

@@
 # calculate mean for each group of stars
-# Tidied csv: review_id, star rating, average sentiment score
 review_scores <- reviews_text %>% 
@@
 Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
-```{r}
-# create summary of words and their average sentiment score in each unique
-# review and filter for >= 500 reviews and >= 10 businesses
-# Tidied csv: word, # of businesses word appears, # of reviews word appears,
-# # of different uses of word, average stars of word
+
+```{r fig.width = 8}
 review_words <- reviews_text %>% 
@@
   inner_join(valence_score, by = "word")
-head(summaries, n = 10)
-```
 
-```{r fig.height = 7, fig.width = 7}
 summaries %>% 
@@
   geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
-  scale_x_log10(limits = c(200, 100000), 
-                breaks = c(1000, 10000), labels = c(1000, 10000)) +
+  scale_x_log10(limits = c(0, 200000)) +
   geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +

### 2016-08-04 eda/sentiment-analysis.Rmd
randomized sample of reviews

--- 2016-08-04 eda/sentiment-analysis.Rmd
@@
 
-I'll read in the first 500,000 observations of the Yelp reviewers data, which has been written to a csv file.
+I'll read 500,000 randomly sampled observations of the Yelp reviewers data, which has been written to a csv file.
 ```{r}
-reviews <- read_csv("../clean_data/reviews.csv")
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
+reviews <- reviews %>% 
+  sample_n(500000)
 ```
@@
 
+Below, I'll plot word frequency vs 
 ```{r fig.height = 7, fig.width = 7}

### 2016-08-05 eda/location-ratings.Rmd
cleaned up data for plotting

--- 2016-08-03 eda/location-ratings.Rmd
@@
 
-I wanted to see if YELP users' review ratings change when they are traveling.
-This required 3 different data sets: business data, reviews data and user data.
+I wanted to see if YELP users' review ratings change when they are traveling. This required 3 different data sets: business data, reviews data and user data. 
+```{r}
+users <- read_csv("../clean_data/yelp_users.csv")
+business <- read_csv("../clean_data/yelp_business.csv")
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
+```
+
 In order to select samples that can represent user trends, 15 users that have most number of reviews were selected.
@@
 ```{r}
-user_reviews <- read_csv("user-reviews.csv")
-ggplot(user_reviews, aes(x = max_review,
-                         y = val)) +
-  geom_bar(stat = "identity", 
-           position = "dodge") + 
-  facet_wrap(~name) + 
-  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
-  xlab("Location") + 
-  ylab("Star Ratings") +
-  scale_x_discrete(labels=c("Travelling", "Home"))
-  scale_x_discrete(labels=c("Travelling", "Home"))
+selected_users <- users %>% 
+  filter(review_count > 100) %>% 
+  select(name, user_id, review_count)
+
+user_reviews <- reviews %>% 
+  select(user_id, review_id, stars, business_id)
+
+business_locations <- business %>% 
+  select(business_id, state)
+
+user_reviews <- left_join(selected_users, user_reviews) %>% 
+  left_join(business_locations) %>% 
+  na.omit
+
+familiar_location <- group_by(user_reviews, user_id, state) %>% 
+  tally()
+
+location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>% 
+  select(-n) %>% 
+  left_join(familiar_location) %>% 
+  mutate(max_review = TRUE)
+
+user_reviews <- left_join(user_reviews, location_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+true_r <- filter(user_reviews, max_review == TRUE)
+
+ggplot() +
 ```

### 2016-08-05 clean_data/CleanData.R

@@ -4,11 +4,16 @@ library(readr)
 
 # Read in raw data convert to data frames
 business <- fromJSON(sprintf("[%s]", 
-                     paste(read_lines(
-                       "../raw_data/yelp_academic_dataset_business.json"), 
-                     collapse = ","))) %>% 
+                             paste(read_lines("yelp_academic_dataset_business.json"), 
+                                   collapse = ","))) %>% 
   flatten() %>% 
-  tbl_df()
+  select(business_id, open, categories, review_count, state, stars, 
+         `attributes.Noise Level`, `attributes.Attire`, `attributes.Take-out`,
+         `attributes.Takes Reservations`, `attributes.Delivery`,
+         `attributes.Outdoor Seating`, `attributes.Accepts Credit Cards`,
+         `attributes.Happy Hour`) %>% 
+  filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
+business <- data.frame(lapply(business, as.character), stringsAsFactors=FALSE)
 
 reviews <- fromJSON(sprintf("[%s]", 
                     paste(read_lines(
@@ -19,10 +24,11 @@ reviews <- fromJSON(sprintf("[%s]",
 
 users <- fromJSON(sprintf("[%s]", 
                   paste(read_lines(
-                    "../raw_data/yelp_academic_dataset_user.json"), 
+                    "yelp_academic_dataset_user.json"), 
                   collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()
+users <- data.frame(lapply(users, as.character), stringsAsFactors=FALSE)
 
 # Write data-frames to csvs
 write_csv(business, "yelp_business.csv")

### 2016-08-05 clean_data/CleanData.R
little change in directory

@@ -4,7 +4,7 @@ library(readr)
 
 # Read in raw data convert to data frames
 business <- fromJSON(sprintf("[%s]", 
-                             paste(read_lines("yelp_academic_dataset_business.json"), 
+                             paste(read_lines("../raw_data/yelp_academic_dataset_business.json"), 
                                    collapse = ","))) %>% 
   flatten() %>% 
   select(business_id, open, categories, review_count, state, stars, 
@@ -24,7 +24,7 @@ reviews <- fromJSON(sprintf("[%s]",
 
 users <- fromJSON(sprintf("[%s]", 
                   paste(read_lines(
-                    "yelp_academic_dataset_user.json"), 
+                    "../raw_data/yelp_academic_dataset_user.json"), 
                   collapse = ","))) %>% 
   flatten() %>% 
   tbl_df()

### 2016-08-05 location.R
location analysis added

@@ -9,15 +9,13 @@ library(maps)
 library(jsonlite)
 
 review <- fromJSON(sprintf("[%s]", 
-                           paste(read_lines("yelp_academic_dataset_review.json", 
-                                            n_max = 1500000), 
+                           paste(readLines("yelp_academic_dataset_review.json"), 
                                  collapse = ","))) %>% 
   select(user_id, review_id, stars, business_id)
 
 
 user <- fromJSON(sprintf("[%s]", 
-                         paste(read_lines("yelp_academic_dataset_user.json",
-                                          n_max = 100000), 
+                         paste(read_lines("yelp_academic_dataset_user.json"), 
                                collapse = ",")))
 
 business_location <- fromJSON(sprintf("[%s]", 
@@ -36,7 +34,7 @@ user_reviews <- left_join(user, review) %>%
 u <- group_by(user_reviews, user_id, city) %>% 
   tally()
 
-max_reviews <- aggregate(n ~ user_id, u, max) %>% 
+max_reviews <- aggregate(n ~ user_id, familiar_location, max) %>% 
   left_join(u) %>% 
   select(-n) %>% 
   mutate(max_review=TRUE)

### 2016-08-05 location.R
deleted unnecessary files

@@ -1,60 +1,0 @@
-library(readr)
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(magrittr)
-library(ggmap)
-
-library(maps)
-library(jsonlite)
-
-review <- fromJSON(sprintf("[%s]", 
-                           paste(readLines("yelp_academic_dataset_review.json"), 
-                                 collapse = ","))) %>% 
-  select(user_id, review_id, stars, business_id)
-
-
-user <- fromJSON(sprintf("[%s]", 
-                         paste(read_lines("yelp_academic_dataset_user.json"), 
-                               collapse = ",")))
-
-business_location <- fromJSON(sprintf("[%s]", 
-                             paste(readLines("yelp_academic_dataset_business.json"), 
-                                   collapse = ","))) %>% 
-  select(business_id, city)
-
-user <- user[order(-user$review_count),] %>% 
-  head(15) %>% 
-  select(name, user_id, review_count)
-
-# Join user and review by user_id
-user_reviews <- left_join(user, review) %>% 
-  left_join(business_location) 
-  
-u <- group_by(user_reviews, user_id, city) %>% 
-  tally()
-
-max_reviews <- aggregate(n ~ user_id, familiar_location, max) %>% 
-  left_join(u) %>% 
-  select(-n) %>% 
-  mutate(max_review=TRUE)
-
-user_reviews <- left_join(user_reviews, max_reviews) 
-user_reviews[is.na(user_reviews)] <- FALSE
-
-user_reviews <- user_reviews %>% 
-  group_by(name, max_review) %>% 
-  summarise(val = mean(stars)) %>% 
-  mutate(count = n()) %>% 
-  filter(count == 2)
-
-ggplot(user_reviews, aes(x = max_review,
-                         y = val)) +
-  geom_bar(stat = "identity", 
-           position = "dodge") + 
-  facet_wrap(~name) + 
-  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
-  xlab("Location") + 
-  ylab("Star Ratings") +
-  scale_x_discrete(labels=c("Travelling", "Home"))
-  scale_x_discrete(labels=c("Travelling", "Home"))

### 2016-08-05 clean_data/CleanData.R
clean_data merge

@@ -8,7 +8,7 @@ business <- fromJSON(sprintf("[%s]",
                        "../raw_data/yelp_academic_dataset_business.json"), 
                      collapse = ","))) %>% 
   flatten() %>% 
-  tbl_df()
+  data.frame()
 
 reviews <- fromJSON(sprintf("[%s]", 
                     paste(read_lines(

### 2016-08-05 eda/business-attributes.Rmd

@@
 attire_type <- read_csv('attire-attr.csv')
+
 states <- map_data('state')

### 2016-08-05 eda/location-ratings.Rmd

@@
 ---
-title: "location-ratings"
+title: "Location Ratings"
+author: "Irene Lee"
 output: html_document
@@
 
-I wanted to see if YELP users' review ratings change when they are traveling. This required 3 different data sets: business data, reviews data and user data. 
+I wanted to see if YELP users' review ratings change when they are traveling.
+This required 3 different data sets: business data, reviews data and user data.
+I read three csv's that had previously been created.
 ```{r}
@@
 
-In order to select samples that can represent user trends, 15 users that have most number of reviews were selected.
-By selecting columns that I need for plots,  three different data tables are joined.
-After grouping by 'user' one location where users are most familiar with is selected and I decided to compare this location to all the other locations.
-I have ignored data table rows that have  same number of reviews for all cities.
+In order to show a good representation of user trends, I have chosen users that have left more than 50 reviews in total.
+I have joined three tables, selected users(review counts over 50), reviews and business locations.
+
+Since I was using an academic data set provided by Yelp, it only contained some amount of user reviews.
+I have filtered the users to those with more than 10 reviews in the actual data set provided.
+I also added a column named 'most_reviewed' which will be true for one state that the user has left most reviews in (the state the user is most familiar with).
+
+The final data set was produced by combining everything above with users' average star rating per state.
 
@@
 selected_users <- users %>% 
-  filter(review_count > 100) %>% 
+  filter(review_count > 50) %>% 
   select(name, user_id, review_count)
@@
 location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
-  select(-n) %>% 
   left_join(familiar_location) %>% 
-  mutate(max_review = TRUE)
+  mutate(most_reviewed = TRUE) %>% 
+  filter(n > 10) %>% 
+  select(-n)
 
@@
 
-true_r <- filter(user_reviews, max_review == TRUE)
+# average stars for unfamiliar/familiar area for a user
+avg_star_reviews <- user_reviews %>% 
+  group_by(user_id, most_reviewed) %>% 
+  summarise(avg_star = mean(stars))
 
-ggplot() +
 ```
@@
 
-Using 'facet_wrap', I was able to plot 11 different bar graphs per user.
-The second bar graph represents mean star rating for one city that the user wrote most reviews in.
-The first bar graph represents every other city the user has reviewed.
+The plot has two histograms, one with user ratings on familiar places and another on unfamiliar places.
+There is a quite noticeable differences between the two overlayed histograms.
+The data is extracted from more than 2 million reviews by users, so it for sure represents the .
+
+```{r}
+ggplot(avg_star_reviews, aes(x = avg_star, 
+              fill = most_reviewed)) + 
+  geom_density(alpha = 0.5,
+               color = NA) +
+  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
+  xlab("Average Star Ratings") + 
+  ylab("Density") +
+  scale_fill_manual(name ="Regions",
+                    values = c("blue", "red"),
+                    labels = c("Familiar", "Unfamiliar"))
+```

### 2016-08-05 paper/paper.Rmd

---
title: "Final Paper"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(maps)
```

## Introduction

introduction here

## Using Yelp Data

The yelp data set \url{http://www.sharelatex.com} consists of information about Yelp users, reviews they wrote and business information.

## Review Clusters in the US

```{r, echo=FALSE}
us_business <- read_csv('us-business.csv')
noise_level <- read_csv('noise-attr.csv') 
attire_type <- read_csv('attire-attr.csv')
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

## Looking at attributes of businesses
```{r, echo=FALSE}
# Noise Level
ggplot(data=noise_level, aes(x = noise_factored,
                            y = star, 
                            fill = state)) +
  geom_bar(stat = "identity", 
           position = "dodge") +
  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
  labs(title = "How Noise Level Influences Average Star Ratings") + 
  xlab("Noise Level") + 
  ylab("Average Star Ratings") +
  guides(fill = guide_legend("Region"))

# Attire type
ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
  geom_bar(stat="identity", position = "dodge") +
  labs(title = "How Attire Influences Average Star Ratings") + 
  xlab("Attire") + 
  ylab("Average Star Ratings") + 
  guides(fill = guide_legend("Region"))

```

```{r, echo=FALSE}
user_reviews <- read_csv("../clean_data/user-reviews.csv")
ggplot(user_reviews, aes(x = max_review,
                         y = val)) +
  geom_bar(stat = "identity", 
           position = "dodge") + 
  facet_wrap(~name) + 
  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
  xlab("Location") + 
  ylab("Star Ratings") +
  scale_x_discrete(labels=c("Travelling", "Home"))
  scale_x_discrete(labels=c("Travelling", "Home"))
```

### 2016-08-05 clean_data/CleanData.R
clean_data

@@ -4,12 +4,11 @@ library(readr)
 
 # Read in raw data convert to data frames
 business <- fromJSON(sprintf("[%s]", 
-                             paste(read_lines("../raw_data/yelp_academic_dataset_business.json"), 
-                                   collapse = ","))) %>% 
+                     paste(read_lines(
+                       "../raw_data/yelp_academic_dataset_business.json"), 
+                     collapse = ","))) %>% 
   flatten() %>% 
-<<<<<<< HEAD
-  data.frame()
-=======
+  data.frame() %>% 
   select(business_id, open, categories, review_count, state, stars, 
          `attributes.Noise Level`, `attributes.Attire`, `attributes.Take-out`,
          `attributes.Takes Reservations`, `attributes.Delivery`,
@@ -17,7 +16,6 @@ business <- fromJSON(sprintf("[%s]",
          `attributes.Happy Hour`) %>% 
   filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
 business <- data.frame(lapply(business, as.character), stringsAsFactors=FALSE)
->>>>>>> f2c09d1744a6671f9355ee7b97639d4970a94b7e
 
 reviews <- fromJSON(sprintf("[%s]", 
                     paste(read_lines(

### 2016-08-05 eda/business-attributes.Rmd
updated business attributes

@@
 
+There were only six states that have businesses reviewed more than 300 times.
+
 ```{r}
-us_business <- read_csv('us-business.csv')
-noise_level <- read_csv('noise-attr.csv') 
-attire_type <- read_csv('attire-attr.csv')
-
-states <- map_data('state')
-ggplot(states) + 
-  geom_polygon(aes(x = long, 
-                   y = lat, 
-                   group = group), 
-               fill = "grey80", 
-               color = "white") + 
-  coord_fixed(1.3) + 
-  geom_point(data = us_business, 
-             aes(long, 
-                 lat, 
-                 color = factor(stars), 
-                 size = count), 
-             alpha = 0.7) + 
-  guides(colour = guide_legend("Star Rating"), 
-         size = guide_legend("Review Counts")) + 
-  labs(title = "Restaurant Reviews in United States") +
-  theme_nothing(legend = TRUE)
+business <- read_csv("../clean_data/yelp_business.csv")
 ```
 
-## Exploring Noise Level
+```{r}
+successful_business <- business %>% 
+  select(-open) %>% 
+  filter(review_count > 300) %>% 
+  group_by(state) %>% 
+  summarise(num = n())
+
+names(business) <- c("id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
+
+ggplot(successful_business, aes(x = reorder(state, -num), 
+                                y= num)) + 
+  geom_bar(stat = "identity", 
+           position = "dodge") +
+  labs(title = "Number of Businesses with more than 300 Reviews") + 
+  xlab("State") + 
+  ylab("Number of Businesses") 
+```
+
+## Exploring Attributes
 
 As expected, restaurants with many reviews and/or high ratings were clustered in specific regions.
-This table shows where most restaurants are clustered around.
-I have chosen 4 regions with most businesses: Nevada, Arizona, North Carolina and Pennsylvania.
 
 ```{r}
-top_data <- us_business %>% 
-  group_by(state) %>% 
-  tally()
-top_data
+business_attributes <- business %>% 
+  filter(count > 300) %>% 
+  select(-open, -count, -categories, -noise, -attire) %>% 
+  gather(key=Attribute, value=Val, -id, -state, -stars) %>% 
+  na.omit
 ```
 
-There were many attributes per restaurant, and some were more influential directly/indirectly to a business' success.
-I have first decided to see how noise level would influcence the star ratings of customers.
-I grouped the data frame by 'state' and 'noise' and created a new column having the average star rating per group.
-The plot didn't know which noise level to plot first, so I have created the factor levels in noise level.
+There were many attributes per restaurant, and some of them were believed to be influential to a business' success.
+I have first chosen six main attributes that seemed critical to the customers' star ratings.
+
+I gathered all the attributes and used facet_wrap to plot six seperate graphs.
+The left chunk represents True and the right represents False.
+There are some states where there's no applicable values for the specific attribute.
 
 ```{r}
-ggplot(data=noise_level, aes(x = noise_factored,
-                            y = star, 
+ggplot(business_attributes, 
+       aes(x = factor(Val, 
+                      levels = c("TRUE","FALSE")), 
+           y = stars, 
            fill = state)) + 
+  facet_wrap(~Attribute) + 
   geom_bar(stat = "identity",
            position = "dodge") +
-  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
-  labs(title = "How Noise Level Influences Average Star Ratings") + 
-  xlab("Noise Level") + 
-  ylab("Average Star Ratings") +
-  guides(fill = guide_legend("Region"))
+  labs(title = "User Ratings on Business Attributes") +
+  xlab("") + 
+  ylab("Star Rating") +
+  scale_fill_discrete(name = "State")
 ```
-
-## Exploring Attire Types
-Now to another business attribute: attire.
-Similar to noise data, attire_data was retrived by grouping the data frame by 'state' and 'attire'.
-Again, the star ratings were the means of each group's star ratings.
-
-```{r}
-ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") +
-  labs(title = "How Attire Influences Average Star Ratings") + 
-  xlab("Attire") + 
-  ylab("Average Star Ratings") + 
-  guides(fill = guide_legend("Region"))
-```

### 2016-08-05 eda/sentiment-analysis.Rmd
accuracy

@@
 Sentiment analysis, or opinion mining, makes use of natural language processing to analyze pieces of text and determine the attitude of the speaker or writer.
-In order to find relevant lexicons to explore this topic with the Yelp review data, I researched different lexicons and found ANEW (Affective Norms for English Words), a "sentiment lexcion" that scores words for valence.
+I researched different lexicons and found ANEW (Affective Norms for English Words), a "sentiment lexcion" that scores words for valence.
 
@@
 
-Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
+Positive correlation exists!
+Some inaccuracy (outliers on boxplots).
+Find out most common positive and negative words in reviews, creating a summary of the counts.
+I filtered for greater than 500 reviews and 10 business so they're not unique words to a local business or rare words with strange sentiments.
 ```{r}
@@
 # Tidied csv: word, # of businesses word appears, # of reviews word appears,
-# # of different uses of word, average stars of word
+# average stars of word
 review_words <- reviews_text %>% 
@@
             reviews = n(),
-            use = sum(n),
             average_star = mean(stars)) %>% 
@@
 
-Below, I'll plot word frequency vs 
+Now, I'll plot word average star rating vs.
+word frequency to see what words scored positive ratings.
+I'll also color by AFINN score to visualize inaccuracies and determine how well they were classified using the mean star rating of all reviews as a baseline metric.
+
 ```{r fig.height = 7, fig.width = 7}
@@
 ```
+Blue words mostly lie above the line and red words lie below so reveiw text is a pretty good predictor of business rating. Let's see how accurate it was.
+
+```{r}
+positive <- summaries %>% 
+  filter(score > 0)
+negative <- summaries %>% 
+  filter(score < 0)
+above <- positive %>% 
+  filter(average_star >= mean(reviews$stars))
+below <- negative %>% 
+  filter(average_star <= mean(reviews$stars))
+percent_pos <- nrow(above) / nrow(positive)
+percent_neg <- nrow(below) / nrow(negative)
+print(str_c("Positivity Accuracy: ", percent_pos))
+print(str_c("Negativity Accuracy: ", percent_neg))
+```
+64.23% of positive words lie above the mean average rating!
+There's definitely a positive correlation between word positivity in text reviews and Yelp business star ratings.
+Word negativity is even better at 87.24% accuracy of negative words lying below the mean average rating.
+
+What's the accuracy for words that are +5 or -5? Do they lead to 5-star ratings?
+```{r}
+pos_five <- summaries %>% filter(score == 5)
+neg_five <- summaries %>% filter(score == -5)
+```

### 2016-08-05 functions/wordcloud.R
layout

@@ -1,6 +1,12 @@
+# Library
 library(wordcloud)
 
-word_cloud <- function(words, frequency, colors) {
+# Functions:
+# Creates word cloud for vector of words, sized and colored by frequency
+# Args: words - vector of words 
+#       frequency - # of reviews word appears in
+#       colors - color scale for word cloud
+WordCloud <- function(words, frequency, colors) {
   wordcloud(words, frequency, scale = c(4, 0.5),
             random.order = F, random.color = F, use.r.layout = T,
             rot.per = 0.35, colors = colors)

### 2016-08-06 eda/sentiment-analysis.Rmd
plots

@@
 library(tm)
+library(ggrepel)
+source("../functions/PercentAccuracy.R")
 ```
@@
   geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
-  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
+  scale_color_gradient2(low = "red", high = "blue", 
+                        midpoint = 0, mid = "grey") +
   labs(x = "# of reviews",
-       y = "Average Stars",
-       color = "AFINN") +
+       y = "Average Yelp Stars",
+       color = "Valence Score") +
+  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
   theme_bw()
 ```
+
 Blue words mostly lie above the line and red words lie below so reveiw text is a pretty good predictor of business rating. Let's see how accurate it was.
@@
   filter(score < 0)
-above <- positive %>% 
-  filter(average_star >= mean(reviews$stars))
-below <- negative %>% 
-  filter(average_star <= mean(reviews$stars))
-percent_pos <- nrow(above) / nrow(positive)
-percent_neg <- nrow(below) / nrow(negative)
+percent_pos <- PercentAccuracy(positive)
+percent_neg <- 1 - PercentAccuracy(negative)
 print(str_c("Positivity Accuracy: ", percent_pos))
@@
 
-What's the accuracy for words that are +5 or -5? Do they lead to 5-star ratings?
-```{r}
-pos_five <- summaries %>% filter(score == 5)
-neg_five <- summaries %>% filter(score == -5)
+```{r fig.height = 7}
+summaries %>% 
+  arrange(desc(reviews)) %>% 
+  ggplot(aes(score, average_star)) +
+  geom_point(aes(size = reviews)) +
+  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
+  geom_smooth(method = "lm", se = FALSE) +
+  xlab("Valence Score") +
+  ylab("Average Yelp Stars") +
+  labs(title = "Average Yelp Star Rating vs. Valence Score") +
+  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
+  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
+  expand_limits(x = -6)
 ```

### 2016-08-06 rscripts/sentiments.R
headers

@@ -1,3 +1,6 @@
+# Sentiment Analysis for Yelp Text Reviews
+# Using tidytext and AFINN lexicon, assign valence score to words in text reviews
+# to classify star ratings of Yelp businesses
 library(jsonlite)
 library(readr)
 library(httr)

### 2016-08-06 eda/word-cloud.Rmd
function

@@
 red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
-word_cloud(one$word, one$n, red)
+WordCloud(one$word, one$n, red)
 green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
            "seagreen", "darkgreen")
-word_cloud(five$word, five$n, green)
+WordCloud(five$word, five$n, green)
 ```

### 2016-08-06 eda/sentiment-analysis.Rmd
formatting and analysis
analysis

@@
 
+write_csv(reviews_text, "../clean_data/reviews_text.csv")
+
 # rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
@@
        y = "Mean Sentiment Score",
-       title = "Mean Sentiment Score vs. Business Star Rating") +
-  theme_bw()
+       title = "Mean Sentiment Score vs. Business Star Rating")
 ```
@@
        color = "Valence Score") +
-  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
-  theme_bw()
+  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1))
 ```
@@
 
+This is pretty informative, but I want to see these words plotted by their valence score and average Yelp rating to visualize if there's a positive correlation here between sentiment score and their star rating.
 ```{r fig.height = 7}
@@
 ```
+
+Based on a simple linear regression line, words with higher scores are clustered towards 4 and 5-star ratings, while most negative words have pretty low average ratings.
+Some words like "damn" had higher star ratings despite their low AFINN score, but that could be explained by reviews where writers could have described their food or service as "damn good".

### 2016-08-07 functions/wordcloud.R
sizing

@@ -7,7 +7,7 @@ library(wordcloud)
 #       frequency - # of reviews word appears in
 #       colors - color scale for word cloud
 WordCloud <- function(words, frequency, colors) {
-  wordcloud(words, frequency, scale = c(4, 0.5),
+  wordcloud(words, frequency, scale = c(2.75, 0.5),
             random.order = F, random.color = F, use.r.layout = T,
             rot.per = 0.35, colors = colors)
 }

### 2016-08-07 paper/paper.Rmd
added sentiment analysis

@@
 library(ggmap)
+library(tidytext)
 library(maps)
+library(extrafont)
+library(wordcloud)
+library(stringr)
+library(purrr)
+source("../functions/WordCloud.R")
+source("../functions/PercentAccuracy.R")
+source("../functions/MeanStar.R")
+font_import()
+loadfonts()
 ```
@@
 
-introduction here
+Whenever a person hears about a business or think about starting their own, they are always told that a business’s success is all about location, location, location.
+It’s hard to quantify how much of a business’s success is determined by its location, but we were curious to see if location was linked to higher star ratings on Yelp.
+Yelp is a service that publishes crowd-sourced reviews about local business online.
+Additionally, we wanted to see if there was any relationship between certain attributes of restaurants and their ratings on Yelp.
 
-## Using Yelp Data
+Aside from analyzing the success and behavior of businesses, we also decided to explore the relationship between the text in reviews and the number of stars it received.
+In our project, we used a deep dataset of Round 7 of the Yelp Academic Dataset challenge, available at: https://www.yelp.com/dataset_challenge/dataset.
+The dataset includes five json files of business, check-in, user, review, and tip data, but our research only involved looking at the business, user, and review datasets.
 
-The yelp data set \url{http://www.sharelatex.com} consists of information about Yelp users, reviews they wrote and business information.
+## Exploring the Data
+###1. Data Properties
+The dataset includes 2.2 million Yelp reviews for 77,455 businesses across the United States.
+To gain access to the dataset, a name and email had to be provided and the terms of use had to be accepted.
+The schematic for the business, user, and review datasets were:
 
-## Review Clusters in the US
+{
+    'type': 'business',
+    'business_id': (encrypted business id),
+    'name': (business name),
+    'neighborhoods': [(hood names)],
+    'full_address': (localized address),
+    'city': (city),
+    'state': (state),
+    'latitude': latitude,
+    'longitude': longitude,
+    'stars': (star rating, rounded to half-stars),
+    'review_count': review count,
+    'categories': [(localized category names)]
+    'open': True / False (corresponds to closed, not business hours),
+    'hours': {
+        (day_of_week): {
+            'open': (HH:MM),
+            'close': (HH:MM)
+        },
+        ...
+    },
+    'attributes': {
+        (attribute_name): (attribute_value),
+        ...
+    },
+}
 
-```{r, echo=FALSE}
-us_business <- read_csv('us-business.csv')
-noise_level <- read_csv('noise-attr.csv') 
-attire_type <- read_csv('attire-attr.csv')
-states <- map_data('state')
-ggplot(states) + 
-  geom_polygon(aes(x = long, 
-                   y = lat, 
-                   group = group), 
-               fill = "grey80", 
-               color = "white") + 
-  coord_fixed(1.3) + 
-  geom_point(data = us_business, 
-             aes(long, 
-                 lat, 
-                 color = factor(stars), 
-                 size = count), 
-             alpha = 0.7) + 
-  guides(colour = guide_legend("Star Rating"), 
-         size = guide_legend("Review Counts")) + 
-  labs(title = "Restaurant Reviews in United States") +
-  theme_nothing(legend = TRUE)
+{
+    'type': 'review',
+    'business_id': (encrypted business id),
+    'user_id': (encrypted user id),
+    'stars': (star rating, rounded to half-stars),
+    'text': (review text),
+    'date': (date, formatted like '2012-03-14'),
+    'votes': {(vote type): (count)},
+}
+
+{
+    'type': 'user',
+    'user_id': (encrypted user id),
+    'name': (first name),
+    'review_count': (review count),
+    'average_stars': (floating point average, like 4.31),
+    'votes': {(vote type): (count)},
+    'friends': [(friend user_ids)],
+    'elite': [(years_elite)],
+    'yelping_since': (date, formatted like '2012-03'),
+    'compliments': {
+        (compliment_type): (num_compliments_of_this_type),
+        ...
+    },
+    'fans': (num_fans),
+}
+
+###2. Data Pre-Processing
+Data pre-processing were the steps taken to collect and prepare the input data for data mining and visualization.
+
+####Stage One: JSON to CSV
+Converting the raw data from JSON was quite easy using R libraries.
+We began by reading in the data and writing the tidied data-frame to CSV objects to be read in our analyses.
+Once this was completed, other R libraries were used to wrangle and tidy the data for their final transformations.
+
+####Stage Two: Data Wrangling
+We began by filtering for businesses with more than 300 reviews in the United States.
+Looking more closely at the business dataset, we noticed a nested data-frame of attributes for each business, so we cleaned and gathered the data so that each row contained one business attribute.
+Business data set was used to see what makes a business popular and successful; especially by looking at where most-reviewed are clustered and the influence of major business attributes.
+
+Review data was cleaned for sentiment analysis using a library called “tidytext”.
+After reading in the review dataset, we randomly sampled 500,000 observations.
+With this, we tokenized each word in a review into a single row in the data-frame and removed stop words like “a”, “and”, “the”, etc.
+since they had no indication of the reviewers’ attitudes.
+Using built-in lexicons, we assigned each word a valence score and computed the mean score for each review.
+Additionally, we created per-word summaries, computing the number of business and reviews the word appeared in and the average star rating based on each review.
+We filtered for words that appeared in more than 10 businesses and 500 reviews to exclude rare words with strange valence scores and ratings.
+Using these cleaned datasets, we were able to create visualizations and make inferences discussed later.
+
+```{r load, echo = FALSE}
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
+reviews <- reviews %>% 
+  sample_n(500000)
 ```
 
-## Looking at attributes of businesses
-```{r, echo=FALSE}
-# Noise Level
-ggplot(data=noise_level, aes(x = noise_factored,
-                            y = star, 
-                            fill = state)) +
-  geom_bar(stat = "identity", 
-           position = "dodge") +
-  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
-  labs(title = "How Noise Level Influences Average Star Ratings") + 
-  xlab("Noise Level") + 
-  ylab("Average Star Ratings") +
-  guides(fill = guide_legend("Region"))
+Lastly, business data, user data and review data were all used to analyze the users’ behaviors when they are in unfamiliar places.
+User data was cleaned to filter for active users with a significant amount of reviews.
+Cleaned review data and business data were then joined together with user data.
+We created an additional boolean column called ‘most_reviewed’, after computing the most familiar location for a user (one state per user where most of his/her reviews reside).
+Using this, we cleaned up and created a new data frame with average star ratings of familiar places and unfamiliar places per user.
+In the next section, we discuss this further along with results.
 
-# Attire type
-ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") +
-  labs(title = "How Attire Influences Average Star Ratings") + 
-  xlab("Attire") + 
-  ylab("Average Star Ratings") + 
-  guides(fill = guide_legend("Region"))
+####Stage Three: Pre-Processing using ‘tidytext’ for Sentiment Analysis
+Sentiment analysis, or opinion mining, makes use of natural language processing to analyze pieces of text and determine the attitude of the speaker or writer.
+To perform sentiment analysis, we researched various text mining libraries.
+First, _tm_ was used to remove stop words, common English words that would give no information, but the process of splitting text reviews into one word-per-row and removing stop words was too inefficient.
+After more research, we came across “tidytext”, a library for text mining.
+Using this library, cleaning and aggregating the review data was extremely easy and efficient.
+We then performed tidy analysis to strip reviews and tokenize each word into a single row in the data-frame.
 
+To explore this data, we researched different lexicons and found ANEW (Affective Norms for English Words), a "sentiment lexicon" that scores words for valence.
+However, upon further research, we came across an article written by Finn Arup Nielsen, where he compares a sentiment lexicon he created to ANEW.
+His lexicon, AFINN, contains a list of English words that are assigned an integer value from -5 (negative) to +5 (positive) based on the word’s sentiment.
+He concluded that his word list better classifies sentiment rating than ANEW on Twitter sentiment analysis.
+Since Yelp text reviews are similar to tweets, we used AFINN for this sentiment analysis.
+
+##Results and Discussion
+####B. Sentiment Analysis
+We hypothesized that words with higher valence scores would produce higher Yelp star ratings for businesses.
+First, using the R library “wordcloud”, we formed two word clouds for the 100 most frequent words in text reviews with one-star and five-star ratings to determine if there was a distinct difference between the words used.
+
+```{r wordcloud, echo = FALSE, message = FALSE}
+reviews_text <- read_csv("../clean_data/reviews_text.csv")
+one <- reviews_text %>% 
+  filter(stars == 1) %>% 
+  group_by(word) %>% 
+  count() %>% 
+  top_n(100) %>% 
+  arrange(n)
+
+five <- reviews_text %>% 
+  filter(stars == 5) %>% 
+  group_by(word) %>% 
+  count() %>% 
+  top_n(100) %>% 
+  arrange(n)
+
+red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
+WordCloud(one$word, one$n, red)
+green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
+           "seagreen", "darkgreen")
+WordCloud(five$word, five$n, green)
 ```
 
-```{r, echo=FALSE}
-user_reviews <- read_csv("../clean_data/user-reviews.csv")
-ggplot(user_reviews, aes(x = max_review,
-                         y = val)) +
-  geom_bar(stat = "identity", 
-           position = "dodge") + 
-  facet_wrap(~name) + 
-  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
-  xlab("Location") + 
-  ylab("Star Ratings") +
-  scale_x_discrete(labels=c("Travelling", "Home"))
-  scale_x_discrete(labels=c("Travelling", "Home"))
+While words like “food” and “service” were the most common, there is a noticeable difference between the two word clouds generated.
+To further explore this difference, we generated boxplots of mean sentiment score versus business star rating to crudely determine if there was a positive trend for valence score and business rating.
+
+```{r boxplots, echo = FALSE, message = FALSE, fig.align = "center"}
+review_scores <- read_csv("../clean_data/review_scores.csv")
+ggplot(review_scores) +
+  geom_boxplot(aes(stars, sentiment, group = stars)) +
+  labs(x = "Business Star Rating",
+       y = "Mean Sentiment Score",
+       title = "Mean Sentiment Score vs. Business Star Rating") +
+  theme(text = element_text(family = "Times New Roman"))
 ```
+
+There was indeed a positive correlation, despite some words with high valence scores appearing in reviews with low ratings and vice versa.
+Now to determine which words were indicative of a positive review and a negative review and the accuracy of our valence score classifier, using the word summaries data we generated a scatterplot labeled by word, colored by AFINN score, and plotted by average star rating versus word frequency.
+Additionally, we overlaid a horizontal line of the mean restaurant rating as a metric to determine the accuracy of our classifier.
+We would expect all words above to be blue and all words below to be red.
+
+```{r afinn, echo = F, message = F, fig.align = "center", fig.height = 6}
+summaries <- read_csv("../clean_data/summaries.csv")
+summaries %>% 
+  ggplot(aes(reviews, average_star, color = score)) +
+  geom_point() +
+  geom_text(aes(label = word, family = "Times New Roman"), 
+            check_overlap = TRUE, vjust = 1, hjust = 1) +
+  scale_x_log10(limits = c(200, 100000), 
+                breaks = c(1000, 10000), labels = c(1000, 10000)) +
+  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
+  scale_color_gradient2(low = "red", high = "blue", 
+                        midpoint = 0, mid = "grey") +
+  labs(x = "# of reviews",
+       y = "Average Yelp Stars",
+       color = "Valence Score") +
+  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
+  theme(text = element_text(family = "Times New Roman"))
+
+positive <- summaries %>% 
+  filter(score > 0)
+negative <- summaries %>% 
+  filter(score < 0)
+percent_pos <- PercentAccuracy(positive)
+percent_neg <- 1 - PercentAccuracy(negative)
+print(str_c("Positivity Accuracy: ", percent_pos))
+print(str_c("Negativity Accuracy: ", percent_neg))
+```
+
+For the most part, our classifier was accurate.
+65.02% of positive words sampled lied above the mean restaurant rating, and even better, 86.99% of negative words lied below the mean star rating.
+Therefore, it seems reasonable to infer that there is indeed a positive correlation between valence score and Yelp business rating.
+
+However, we also wanted to see these words plotted by their valence score versus average star rating to visualize the actual trend between sentiment and rating, rather than just viewing what percentage of words lied above the mean rating.
+```{r trend, echo = FALSE, message = F, fig.align = "center"}
+summaries %>% 
+  arrange(desc(reviews)) %>% 
+  ggplot(aes(score, average_star)) +
+  geom_point(aes(size = reviews)) +
+  geom_text(aes(label = word, family = "Times New Roman"),
+            vjust = 1, hjust = 1, check_overlap = TRUE) +
+  geom_smooth(method = "lm", se = FALSE) +
+  xlab("Valence Score") +
+  ylab("Average Yelp Stars") +
+  labs(title = "Average Yelp Star Rating vs. Valence Score") +
+  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
+  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
+  expand_limits(x = -6) +
+  theme(text = element_text(family = "Times New Roman"))
+```
+
+Based on a simple linear regression line, words with higher scores are clustered towards 4 and 5-star ratings, while most negative words have pretty low average ratings.
+Some words like "damn" had higher star ratings despite their low AFINN score, but that could be attributed to writers' different expressions like "damn good" for really good food.
+
+Lastly, we wanted to see what the mean rating was for each AFINN score since that would clearly indicate a correlation.
+
+```{r bar, echo = F, message = F, fig.align = "center"}
+data.frame(
+  x = factor(-5:5), 
+  y = unlist(-5:5 %>% map(MeanStar))) %>% 
+  filter(!is.nan(y)) %>% 
+  ggplot(aes(x = x, y = y, fill = x)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Valence Score",
+       y = "Average Star Rating",
+       fill = "Valence Score") +
+  theme(text = element_text(family = "Times New Roman"))
+```
+
+As expected, higher AFINN scores did in fact result in higher mean business ratings.

### 2016-08-07 eda/business-attributes.Rmd
cleaned

@@
 
-```{r}
+```{r, echo = FALSE}
 ggplot(business_attributes, 

### 2016-08-07 paper/paper.Rmd
cleaned

--- 2016-08-05 paper/paper.Rmd
@@
 
-The yelp data set \url{http://www.sharelatex.com} consists of information about Yelp users, reviews they wrote and business information.
-
-## Review Clusters in the US
+The yelp data set (\url{https://www.yelp.com/dataset_challenge}) consists of information about Yelp users, reviews they wrote and business information.
 
 ```{r, echo=FALSE}
-us_business <- read_csv('us-business.csv')
-noise_level <- read_csv('noise-attr.csv') 
-attire_type <- read_csv('attire-attr.csv')
-states <- map_data('state')
-ggplot(states) + 
-  geom_polygon(aes(x = long, 
-                   y = lat, 
-                   group = group), 
-               fill = "grey80", 
-               color = "white") + 
-  coord_fixed(1.3) + 
-  geom_point(data = us_business, 
-             aes(long, 
-                 lat, 
-                 color = factor(stars), 
-                 size = count), 
-             alpha = 0.7) + 
-  guides(colour = guide_legend("Star Rating"), 
-         size = guide_legend("Review Counts")) + 
-  labs(title = "Restaurant Reviews in United States") +
-  theme_nothing(legend = TRUE)
+users <- read_csv("../clean_data/yelp_users.csv")
+business <- read_csv("../clean_data/yelp_business.csv")
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
 ```
 
-## Looking at attributes of businesses
+## Business Clusters in the US
+
+The business data set provided 77,445 rows of information such as review counts, ratings and locations of local businesses.
+After carefully looking at the data set, we have decided to filter out the more significant data by limiting it to businesses having more than 300 reviews in the US.
+
+We have first tried to plot this information with points on a map.
+Points with different sizes stacked up on each other and unexpectedly, the size and color of the points did not tell much information.
+Even though 900+ points were plotted, there were six clusters of points and there was no point of having so many individual points.
+
+Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews.
+There were 6 distinct regions in total.
+Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were clustered in Nevada area and another 31% was in Arizona.
+
+We have hypothesized earlier that location will influence a business’ success. The plot shows
+
 ```{r, echo=FALSE}
-# Noise Level
-ggplot(data=noise_level, aes(x = noise_factored,
-                            y = star, 
-                            fill = state)) +
+successful_business <- business %>% 
+  select(-open) %>% 
+  filter(review_count > 300) %>% 
+  group_by(state) %>% 
+  summarise(num = n())
+
+names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
+
+ggplot(successful_business, aes(x = reorder(state, -num), 
+                                y= num)) + 
   geom_bar(stat = "identity", 
            position = "dodge") +
-  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
-  labs(title = "How Noise Level Influences Average Star Ratings") + 
-  xlab("Noise Level") + 
-  ylab("Average Star Ratings") +
-  guides(fill = guide_legend("Region"))
-
-# Attire type
-ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
-  geom_bar(stat="identity", position = "dodge") +
-  labs(title = "How Attire Influences Average Star Ratings") + 
-  xlab("Attire") + 
-  ylab("Average Star Ratings") + 
-  guides(fill = guide_legend("Region"))
+  labs(title = "Number of Businesses with more than 300 Reviews") + 
+  xlab("State") + 
+  ylab("Number of Businesses")
 
@@
 
-```{r, echo=FALSE}
-user_reviews <- read_csv("../clean_data/user-reviews.csv")
-ggplot(user_reviews, aes(x = max_review,
-                         y = val)) +
+## Business Attributes
+
+Looking more into the data set, we wanted to know if certain attributes in specific regions make businesses stand out.
+The business data set is now cleaned and gathered in order to make each row contain one business attribute.
+
+We have first tried to include only two representative plots.
+However, subsetting too much of the data set made us lose many valuable information., It could also potentially lead to overgeneralization.
+
+We wanted to see if any of the attributes of the businesses makes them successful.
+Six major attributes were chosen among many.
+There were slight differences in some categories.
+For example, businesses that accept credit cards seem to have higher ratings compared to those that don't.
+There were no major findings from the plots, however.
+
+Except for slight differences in average ratings, there was no exceptional difference shown among the choices.
+The user review ratings were evenly spread out no matter the specific attribute exists or not.
+The result points out that business attributes do not have huge influences over user ratings.
+
+```{r, echo = FALSE}
+business_attributes <- business %>% 
+  filter(count > 300) %>% 
+  select(-open, -count, -categories, -noise, -attire) %>% 
+  gather(key=Attribute, value=Val, -business_id, -state, -stars) %>% 
+  na.omit
+```
+```{r, echo = FALSE}
+ggplot(business_attributes, 
+       aes(x = factor(Val, 
+                      levels = c("TRUE","FALSE")), 
+           y = stars, 
+           fill = state)) + 
+  facet_wrap(~Attribute) + 
   geom_bar(stat = "identity",
            position = "dodge") +
-  facet_wrap(~name) + 
+  labs(title = "User Ratings on Business Attributes") +
+  xlab("") + 
+  ylab("Star Rating") +
+  scale_fill_discrete(name = "State")
+```
+
+## Users Behavior Changes When Travelling
+
+If business attributes do not impact business' success, then what would?
+
+From analyzing over 2 million reviews, we wanted to find out what would affect people's behavior of rating businesses.
+Since the data set given by Yelp was academic, this did not include every single review by every user in data.
+We have focused on active users that have written more than 50 reviews in total and have 10 reviews in the data provided at the same time.
+This seemed enough to analyze the user trends.
+
+First, we went with facet_wrap in plot after selecting top 15 influencers with most reviews.
+However, since facet focuses rather on individual data than overall trends, it was hard to generalize the findings.
+Some individual preferences were really different from others.
+
+Another approach we took was to plot everyone's ratings into the histograms.
+From the filtered user data set from above, one familiar region was chosen per user.
+This was based on where the user wrote most reviews.
+Two average star ratings were calculated for a user: one for reviews in familiar state and another from reviews when travelling unfamiliar places.
+The results are shown below in density curves.
+
+At initial observation, the density curve for unfamiliar region is smooth and the majority of users tend to give star ratings in between 3 to 4.5 out of 5.
+Number of people giving 1 or 2 stars while traveling is barely seen.
+On the other hand, the ratings in familiar places were rather widely distributed.
+There were good amount of people giving star ratings from 1 through 5, even though the peak of the curve is around 4.
+
+Interestingly, the mean value of each place turned out to be 3.718 for unfamiliar and 3.762 for familiar places.
+However, the standard deviation for the familiar place plot is 0.41 and unfamiliar one is 1.37 so that star ratings for unfamiliar places looked higher at first.
+
+```{r, echo = FALSE}
+selected_users <- users %>% 
+  filter(review_count > 50) %>% 
+  select(name, user_id, review_count)
+
+user_reviews <- reviews %>% 
+  select(user_id, review_id, stars, business_id)
+
+business_locations <- business %>% 
+  select(business_id, state)
+
+user_reviews <- left_join(selected_users, user_reviews) %>% 
+  left_join(business_locations) %>% 
+  na.omit
+
+familiar_location <- group_by(user_reviews, user_id, state) %>% 
+  tally()
+
+location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
+  left_join(familiar_location) %>% 
+  mutate(most_reviewed = TRUE) %>% 
+  filter(n > 10) %>% 
+  select(-n)
+
+user_reviews <- left_join(user_reviews, location_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+# average stars for unfamiliar/familiar area for a user
+avg_star_reviews <- user_reviews %>% 
+  group_by(user_id, most_reviewed) %>% 
+  summarise(avg_star = mean(stars))
+
+ggplot(avg_star_reviews, aes(x = avg_star, 
+              fill = most_reviewed)) + 
+  geom_density(alpha = 0.5,
+               color = NA) +
   labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
-  xlab("Location") + 
-  ylab("Star Ratings") +
-  scale_x_discrete(labels=c("Travelling", "Home"))
-  scale_x_discrete(labels=c("Travelling", "Home"))
+  xlab("Average Star Ratings") + 
+  ylab("Density") +
+  scale_fill_manual(name ="Regions",
+                    values = c("blue", "red"),
+                    labels = c("Familiar", "Unfamiliar"))
 ```

### 2016-08-08 eda/sentiment-analysis.Rmd

@@
 library(tm)
-library(ggrepel)
+library(purrr)
 source("../functions/PercentAccuracy.R")
+source("../functions/MeanStar.R")
 ```
@@
 
-Too slow. I'll try the library __tidytext__. This library also let's me generate valence scores using the AFINN library without having to write an unnecessarily long function.
+Too slow. I'll try the library __tidytext__. This library also let's me generate valence scores using the AFINN library without mhaving to write an unnecessarily long function.
 
@@
 # unnest_tokens splits column into tokens using tokenizers package
-# splits "text" column into individual words to analyze sentiment for further
+# splits "text" column into individual words to nalyze sentiment for further
 # exploration
@@
 
-# calculate mean for each group of stars
-# Tidied csv: review_id, star rating, average sentiment score
+# calculate mean for each review
+# Tidied: review_id, star rating, average sentiment score
 review_scores <- reviews_text %>% 
@@
   summarise(sentiment = mean(score))
+write_csv(review_scores, "../clean_data/review_scores.csv")
 ```
@@
 # review and filter for >= 500 reviews and >= 10 businesses
-# Tidied csv: word, # of businesses word appears, # of reviews word appears,
+# Tidied: word, # of businesses word appears, # of reviews word appears,
 # average stars of word
@@
 head(summaries, n = 10)
+write_csv(summaries, "../clean_data/summaries.csv")
 ```
@@
 ```
-64.23% of positive words lie above the mean average rating!
+63.71% of positive words lie above the mean average rating!
 There's definitely a positive correlation between word positivity in text reviews and Yelp business star ratings.
-Word negativity is even better at 87.24% accuracy of negative words lying below the mean average rating.
+Word negativity is even better at 87.76% accuracy of negative words lying below the mean average rating.
 
@@
 Some words like "damn" had higher star ratings despite their low AFINN score, but that could be explained by reviews where writers could have described their food or service as "damn good".
+
+```{r}
+data.frame(
+  x = factor(-5:5), 
+  y = unlist(-5:5 %>% map(MeanStar))) %>% 
+  filter(!is.nan(y)) %>% 
+  ggplot(aes(x = x, y = y, fill = x)) +
+  geom_bar(stat = "identity") +
+  labs(x = "Valence Score",
+       y = "Average Star Rating",
+       fill = "Valence Score")
+```

### 2016-08-08 paper/paper.Rmd
paper not added in prev commit

--- 2016-08-07 paper/paper.Rmd
@@
 Business data set was used to see what makes a business popular and successful; especially by looking at where most-reviewed are clustered and the influence of major business attributes.
-
+```{r load, echo = FALSE}
+business <- read_csv("../clean_data/yelp_business.csv")
+names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
+successful_business <- business %>% 
+  select(-open) %>% 
+  filter(review_count > 300) %>% 
+  group_by(state) %>% 
+  summarise(num = n())
+```
 Review data was cleaned for sentiment analysis using a library called “tidytext”.
@@
 In the next section, we discuss this further along with results.
-
+```{r load, echo = FALSE}
+users <- read_csv("../clean_data/yelp_users.csv")
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
+```
 ####Stage Three: Pre-Processing using ‘tidytext’ for Sentiment Analysis
@@
 ##Results and Discussion
+
+####A. Location and Business Attributes Analysis
+
+Our first hypothesis was that successful businesses would be clustered at certain points.
+We first tried to plot this information with points on a map using longitude and latitude of the businesses.
+Points with different sizes stacked up on each other and unexpectedly, and the size and color of the points did not tell much information.
+Even though 900+ points were plotted, there were six primary clusters of points and there was no point in having so many individual points.
+
+Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews.
+There were 6 distinct regions in total.
+Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
+```{r, echo = FALSE}
+ggplot(successful_business, aes(x = reorder(state, -num), 
+                                y= num)) + 
+  geom_bar(stat = "identity", 
+           position = "dodge") +
+  labs(title = "Number of Businesses with more than 300 Reviews") + 
+  xlab("State") + 
+  ylab("Number of Businesses") 
+```
+We also hypothesized that there would be business attributes that help business to succeed in terms of number of reviews and ratings.
+We first tried to include two representative plots, ‘Noise Level’ and ‘Attire Type’.
+However, subsetting too much of the data set made us lose valuable information about the dataset.
+Choosing only two random attributes and analyzing was too narrow an exploration of the data.
+
+As such, six major attributes were chosen.
+There were slight differences in star ratings based on some categories.
+For example, businesses that accept credit cards seemed to have higher ratings compared to those that don't.
+Interestingly, restaurants that do not offer delivery showed slightly higher star ratings than those who do.
+There were no major findings from the plots, however.
+Except for slight differences in average ratings of certain attributes, there was no significant difference evident.
+The user review ratings were evenly spread out even if the specific attribute existed or not.
+Our findings pointed out that business attributes do not have huge influences over user ratings.
+```{r, echo = FALSE}
+business_attributes <- business %>% 
+filter(count > 300) %>% 
+select(-open, -count, -categories, -noise, -attire) %>% 
+gather(key=Attribute, value=Val, -business_id, -state, -stars) %>% 
+na.omit
+
+ggplot(business_attributes, 
+aes(x = factor(Val, 
+levels = c("TRUE","FALSE")), 
+y = stars, 
+fill = state)) + 
+facet_wrap(~Attribute) + 
+geom_bar(stat = "identity",
+position = "dodge") +
+labs(title = "User Ratings on Business Attributes") +
+xlab("") + 
+ylab("Star Rating") +
+scale_fill_discrete(name = "State")
+```
 ####B. Sentiment Analysis
@@
 As expected, higher AFINN scores did in fact result in higher mean business ratings.
+
+####C. User Behavior Analysis
+
+From analyzing over 2 million reviews, we wanted to find out what would affect people's behavior of rating businesses.
+Since the data set given by Yelp was academic, this did not include every single review by every user in data.
+We have focused on active users that have written more than 50 reviews in total and have 10 reviews in the data provided at the same time.
+This seemed enough to analyze the user trends.
+
+We have hypothesized that users would give relatively higher star ratings than when visiting local restaurants that they are familiar with.
+
+First, we went with facet_wrap in plot after selecting top 15 influencers with most reviews.
+However, since facet focuses rather on individual data than overall trends, it was hard to generalize the findings.
+Some individual preferences were really different from others.
+
+Another approach we took was to plot everyone's ratings into the histograms.
+From the filtered user data set from above, one familiar region was chosen per user.
+This was based on where the user wrote most reviews.
+Two average star ratings were calculated for a user: one for reviews in familiar state and another from reviews when travelling unfamiliar places.
+The results are shown below in density curves.
+
+At initial observation, the density curve for unfamiliar region is smooth and the majority of users tend to give star ratings in between 3 to 4.5 out of 5.
+Number of people giving 1 or 2 stars while traveling is barely seen.
+On the other hand, the ratings in familiar places were rather widely distributed.
+There were good amount of people giving star ratings from 1 through 5, even though the peak of the curve is around 4.
+
+Interestingly, the mean value of each place turned out to be 3.718 for unfamiliar and 3.762 for familiar places.
+However, the standard deviation for the familiar place plot is 0.41 and unfamiliar one is 1.37 so that star ratings for unfamiliar places looked higher at first.
+
+```{r, echo = FALSE}
+selected_users <- users %>% 
+  filter(review_count > 50) %>% 
+  select(name, user_id, review_count)
+
+user_reviews <- reviews %>% 
+  select(user_id, review_id, stars, business_id)
+
+business_locations <- business %>% 
+  select(business_id, state)
+
+user_reviews <- left_join(selected_users, user_reviews) %>% 
+  left_join(business_locations) %>% 
+  na.omit
+
+familiar_location <- group_by(user_reviews, user_id, state) %>% 
+  tally()
+
+location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
+  left_join(familiar_location) %>% 
+  mutate(most_reviewed = TRUE) %>% 
+  filter(n > 10) %>% 
+  select(-n)
+
+user_reviews <- left_join(user_reviews, location_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+# average stars for unfamiliar/familiar area for a user
+avg_star_reviews <- user_reviews %>% 
+  group_by(user_id, most_reviewed) %>% 
+  summarise(avg_star = mean(stars))
+
+ggplot(avg_star_reviews, aes(x = avg_star, 
+                             fill = most_reviewed)) + 
+  geom_density(alpha = 0.5,
+               color = NA) +
+  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
+  xlab("Average Star Ratings") + 
+  ylab("Density") +
+  scale_fill_manual(name ="Regions",
+                    values = c("blue", "red"),
+                    labels = c("Familiar", "Unfamiliar"))
+```

### 2016-08-08 paper/paper.Rmd
merging

--- 2016-08-07 paper/paper.Rmd
@@
 However, we also wanted to see these words plotted by their valence score versus average star rating to visualize the actual trend between sentiment and rating, rather than just viewing what percentage of words lied above the mean rating.
+
 ```{r trend, echo = FALSE, message = F, fig.align = "center"}
@@
 Lastly, we wanted to see what the mean rating was for each AFINN score since that would clearly indicate a correlation.
+We expected that lower scores would have lower mean business ratings, and higher scores would have higher mean ratings.
 
@@
 As expected, higher AFINN scores did in fact result in higher mean business ratings.
+Interestingly, words with a -5 AFINN rating had a higher rating than words with a -4 and -3 AFINN rating.
+We're not exactly sure what would've caused this, but it seems like an interesting thing to explore for further research.

### 2016-08-08 paper/paper.Rmd
finished paper

@@
 Additionally, we wanted to see if there was any relationship between certain attributes of restaurants and their ratings on Yelp.
+Addiontally, we wanted to explore the the behavior of reviewers when they travel to places outside their "home" location.
 
-Aside from analyzing the success and behavior of businesses, we also decided to explore the relationship between the text in reviews and the number of stars it received.
-In our project, we used a deep dataset of Round 7 of the Yelp Academic Dataset challenge, available at: https://www.yelp.com/dataset_challenge/dataset.
+Aside from analyzing the success and behavior of reviewers and businesses, we also decided to explore the relationship between the text in reviews and the number of stars it received.
+In our project, we used a deep dataset of Round 7 of the Yelp Academic Dataset challenge, available at: [https://www.yelp.com/dataset_challenge/dataset].
 The dataset includes five json files of business, check-in, user, review, and tip data, but our research only involved looking at the business, user, and review datasets.
@@
 Business data set was used to see what makes a business popular and successful; especially by looking at where most-reviewed are clustered and the influence of major business attributes.
-
+```{r load_business, echo = FALSE}
+business <- read_csv("../clean_data/yelp_business.csv")
+names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
+successful_business <- business %>% 
+  select(-open) %>% 
+  filter(count > 300) %>% 
+  group_by(state) %>% 
+  summarise(num = n())
+```
 Review data was cleaned for sentiment analysis using a library called “tidytext”.
 After reading in the review dataset, we randomly sampled 500,000 observations.
-With this, we tokenized each word in a review into a single row in the data-frame and removed stop words like “a”, “and”, “the”, etc.
+With this, we tokenized each word in a text review into a single row in the data-frame and removed stop words like “a”, “and”, “the”, etc.
 since they had no indication of the reviewers’ attitudes.
@@
 
-```{r load, echo = FALSE}
+```{r load_reviews, echo = FALSE}
 reviews <- read_csv("../clean_data/yelp_reviews.csv")
-reviews <- reviews %>% 
+reviews_sample <- reviews %>% 
   sample_n(500000)
@@
 
-Lastly, business data, user data and review data were all used to analyze the users’ behaviors when they are in unfamiliar places.
-User data was cleaned to filter for active users with a significant amount of reviews.
+Lastly, business data, user data and review data were all used to analyze the users’ behaviors when they are in unfamiliar locations User data was cleaned to filter for active users with a significant amount of reviews.
 Cleaned review data and business data were then joined together with user data.
-We created an additional boolean column called ‘most_reviewed’, after computing the most familiar location for a user (one state per user where most of his/her reviews reside).
+We created an additional boolean column called ‘most_revieSwed’, after computing a user's "home" (state where they reviewed the most).
 Using this, we cleaned up and created a new data frame with average star ratings of familiar places and unfamiliar places per user.
 In the next section, we discuss this further along with results.
-
+```{r load_users, echo = FALSE}
+users <- read_csv("../clean_data/yelp_users.csv")
+reviews <- read_csv("../clean_data/yelp_reviews.csv")
+```
 ####Stage Three: Pre-Processing using ‘tidytext’ for Sentiment Analysis
@@
 To perform sentiment analysis, we researched various text mining libraries.
-First, _tm_ was used to remove stop words, common English words that would give no information, but the process of splitting text reviews into one word-per-row and removing stop words was too inefficient.
-After more research, we came across “tidytext”, a library for text mining.
+First, "__tm__" was used to remove stop words, common English words that would give no information, but the process of splitting text reviews into one word-per-row and removing stop words was too inefficient.
+After more research, we came across “__tidytext__”, a library for text mining.
 Using this library, cleaning and aggregating the review data was extremely easy and efficient.
@@
 ##Results and Discussion
+
+####A. Location Mining and Business Attributes
+
+Our first hypothesis was that successful businesses would be clustered at certain points.
+We first tried to plot this information with points on a map using longitude and latitude of the businesses.
+Points with different sizes stacked up on each other, so the size and color of the points did not tell much information.
+Even though 900+ points were plotted, there were really only six primary clusters of points so there was no point in having so many small individual points.
+
+Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews.
+There were 6 distinct regions in total.
+Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
+```{r business, echo = FALSE, fig.align = "center"}
+ggplot(successful_business, aes(x = reorder(state, -num), 
+                                y= num)) + 
+  geom_bar(stat = "identity", 
+           position = "dodge") +
+  xlab("State") + 
+  ylab("Number of Businesses") +
+  theme(text = element_text(family = "Times New Roman"))
+```
+
+\begin{center}
+\textbf{Figure 1:} Number of businesses with more than 300 reviews
+\end{center}
+
+We also hypothesized that there were certain business attributes that would help businesses succeed in terms of number of reviews and ratings.
+We first tried to include two representative plots, ‘Noise Level’ and ‘Attire Type’.
+However, subsetting too much of the data set made us lose valuable information about the dataset.
+Choosing only two random attributes and analyzing was too narrow an exploration of the data.
+
+As such, six major attributes were chosen.
+There were slight differences in star ratings based on some categories.
+For example, businesses that accept credit cards seemed to have higher ratings compared to those that don't.
+Interestingly, restaurants that do not offer delivery showed slightly higher star ratings than those who do.
+There were no major findings from the plots, however.
+Except for slight differences in average ratings of certain attributes, there was no significant difference evident.
+The user review ratings were evenly spread out even if the specific attribute existed or not.
+Our findings pointed out that business attributes do not have huge influences over user ratings.
+```{r attributes, echo = FALSE, fig.align = "center"}
+business_attributes <- business %>% 
+  filter(count > 300) %>% 
+  select(-open, -count, -categories, -noise, -attire) %>% 
+  gather(key = Attribute, value = Val, -business_id, -state, -stars) %>% 
+  na.omit
+
+ggplot(business_attributes, 
+  aes(x = factor(Val, levels = c("TRUE","FALSE")), y = stars, fill = state)) + 
+  facet_wrap(~Attribute) + 
+  geom_bar(stat = "identity", position = "dodge") +
+  xlab("") + 
+  ylab("Star Rating") +
+  scale_fill_discrete(name = "State") +
+  theme(text = element_text(family = "Times New Roman"))
+```
+
+\begin{center}
+\textbf{Figure 2:} User ratings on business attributes
+\end{center}
+
 ####B. Sentiment Analysis
@@
 
-```{r wordcloud, echo = FALSE, message = FALSE}
+```{r wordcloud, echo = FALSE, message = FALSE, fig.height = 3.5}
 reviews_text <- read_csv("../clean_data/reviews_text.csv")
@@
 
+\begin{center}
+\textbf{Figure 3:} 100 most common words for one-star and five-star rated businesses
+\end{center}
+
 While words like “food” and “service” were the most common, there is a noticeable difference between the two word clouds generated.
@@
   labs(x = "Business Star Rating",
-       y = "Mean Sentiment Score",
-       title = "Mean Sentiment Score vs. Business Star Rating") +
+       y = "Mean Sentiment Score") +
   theme(text = element_text(family = "Times New Roman"))
 ```
+\begin{center}
+\textbf{Figure 4:} Mean Sentiment Score vs. Business Star Rating
+\end{center}
 
@@
                 breaks = c(1000, 10000), labels = c(1000, 10000)) +
-  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
+  geom_hline(yintercept = mean(reviews_sample$stars), color = "black", lty = 2) +
   scale_color_gradient2(low = "red", high = "blue", 
@@
 ```
+\begin{center}
+\textbf{Figure 5:} Average Yelp Rating vs. Frequency of Words
+\end{center}
 
 For the most part, our classifier was accurate.
-65.02% of positive words sampled lied above the mean restaurant rating, and even better, 86.99% of negative words lied below the mean star rating.
+65.02% of positive words sampled lied above the mean restaurant rating, and even better, 86.59% of negative words lied below the mean star rating.
 Therefore, it seems reasonable to infer that there is indeed a positive correlation between valence score and Yelp business rating.
@@
   ylab("Average Yelp Stars") +
-  labs(title = "Average Yelp Star Rating vs. Valence Score") +
   scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
@@
 ```
+\begin{center}
+\textbf{Figure 6:} Average Yelp Star Rating vs. Valence Score
+\end{center}
 
@@
 ```
+\begin{center}
+\textbf{Figure 7:} Bar Graph of Average Yelp Rating per AFINN sentiment score
+\end{center}
 
@@
 We're not exactly sure what would've caused this, but it seems like an interesting thing to explore for further research.
+
+####C. User Behavior when Travelling
+
+Looking at the user and review datasets combined, we wanted to find out what would affect people's behavior of rating businesses.
+Since the dataset given by Yelp was academic, this did not include every single review by every user in data.
+We filtered to focus on active users that have written more than 50 reviews in total and have 10 reviews.
+This seemed like a reasonable constraint on the data that would remove any outlier behavior and would still capture the overall trend in user behavior when travelling.
+
+We hypothesized that users would give relatively higher star ratings when travelling than when visiting local restaurants that they are familiar with.
+
+First, we faceted the graph after selecting the top 15 users with most reviews.
+However, since facet focuses rather on individual data than overall trends, it was hard to conceputalize the findings.
+Individual patterns varied, so to capture the overall trend, we plotted their behaviors into one graph.
+
+Another approach we took was to plot users' ratings in a histogram.
+From the filtered user dataset, one familiar region was chosen per user.
+This was based on where the user wrote the most reviews.
+Two average star ratings were calculated for a user: one for reviews in familiar state and another from reviews when travelling to unfamiliar places.
+The best visualization for such a graph was using a density plot, shown below.
+
+```{r density, echo = FALSE, fig.align = "center"}
+selected_users <- users %>% 
+  filter(review_count > 50) %>% 
+  select(name, user_id, review_count)
+
+user_reviews <- reviews %>% 
+  select(user_id, review_id, stars, business_id)
+
+business_locations <- business %>% 
+  select(business_id, state)
+
+user_reviews <- left_join(selected_users, user_reviews) %>% 
+  left_join(business_locations) %>% 
+  na.omit
+
+familiar_location <- group_by(user_reviews, user_id, state) %>% 
+  tally()
+
+location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%
+  left_join(familiar_location) %>% 
+  mutate(most_reviewed = TRUE) %>% 
+  filter(n > 10) %>% 
+  select(-n)
+
+user_reviews <- left_join(user_reviews, location_reviews) 
+user_reviews[is.na(user_reviews)] <- FALSE
+
+# average stars for unfamiliar/familiar area for a user
+avg_star_reviews <- user_reviews %>% 
+  group_by(user_id, most_reviewed) %>% 
+  summarise(avg_star = mean(stars))
+
+ggplot(avg_star_reviews, aes(x = avg_star, 
+                             fill = most_reviewed)) + 
+  geom_density(alpha = 0.5,
+               color = NA) +
+  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
+  xlab("Average Star Ratings") + 
+  ylab("Density") +
+  scale_fill_manual(name ="Regions",
+                    values = c("blue", "red"),
+                    labels = c("Familiar", "Unfamiliar"))
+```
+\begin{center}
+\textbf{Figure 8: "Reviewers' Behavior Changes When In Unfamilar Locations"}
+\end{center}
+
+The density curve for unfamiliar region is smooth and the majority of users tend to give star ratings in between 3 to 4.5 out of 5.
+Number of people giving 1 or 2 stars while traveling is barely seen.
+On the other hand, the ratings in familiar places were rather widely distributed.
+There was a significant portion of users giving star ratings from 1 through 5, even though the peak of the curve is around 4.
+
+The mean rating was 3.718 for unfamiliar and 3.762 for familiar places.
+However, the standard deviation for the familiar locations plot was 0.41, and unfamiliar one was 1.37 so star rating, explained by the variablity between users who travelled.
+
+##Conclusion
+In conclusion, we investigated several questions related to the Yelp datasets, and our results were promising.
+
+Using natural language processing and text mining, we confirmed our original hypothesis that a positive correlation exists between AFINN sentiment score and star rating.
+86.59% of words with negative scores appeared in reviews that were below the mean rating of all reviews from our sample.
+
+##Future Work
+We would use cross-validation to create a training set and test set for our sample of reviews from the dataset.
+We can create a classifier using sentiment analysis and test our trained classifier against the test set to predict business ratings based on the text of the reviews.
+Additionally, we could look at possible correlations between restaurant reviews and ratings and tips, looking at the tips data provided with the dataset.

### 2016-08-08 clean_data/CleanData.R
cleaning business

@@ -16,10 +16,10 @@ business <- fromJSON(sprintf("[%s]",
   flatten() %>% 
   data.frame() %>% 
   select(business_id, open, categories, review_count, state, stars, 
-         `attributes.Noise Level`, `attributes.Attire`, `attributes.Take-out`,
-         `attributes.Takes Reservations`, `attributes.Delivery`,
-         `attributes.Outdoor Seating`, `attributes.Accepts Credit Cards`,
-         `attributes.Happy Hour`) %>% 
+         `attributes.Noise.Level`, `attributes.Attire`, `attributes.Take.out`,
+         `attributes.Takes.Reservations`, `attributes.Delivery`,
+         `attributes.Outdoor.Seating`, `attributes.Accepts.Credit.Cards`,
+         `attributes.Happy.Hour`) %>% 
   filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
 business <- data.frame(lapply(business, as.character), stringsAsFactors=FALSE)
 

### 2016-08-09 eda/business-attributes.Rmd
explanations added to rmds

@@
 ```{r}
+# Filters out businesses with more than 300 reviews
+# Gets the number of businesses in such category grouping by state.
 successful_business <- business %>% 

### 2016-08-09 eda/location-ratings.Rmd
explanations added to rmds

@@
 ```{r}
+# Users wrote >= 50 reviews
 selected_users <- users %>% 
@@
 
+# Cleaned review data
 user_reviews <- reviews %>% 
@@
 
+# Cleaned business data
 business_locations <- business %>% 
@@
 
+# Selected user data joined with review and business data
 user_reviews <- left_join(selected_users, user_reviews) %>% 
@@
 
+# Computed each number of reviews a user wrote in each state
 familiar_location <- group_by(user_reviews, user_id, state) %>% 
@@
 
+# 
 location_reviews <- aggregate(n ~ user_id, familiar_location, max) %>%

### 2016-08-09 paper/paper.Rmd
explanations added to rmds

@@
   summarise(num = n())
+ratings_business <- business %>% 
+  select(business_id, state, stars, count)
 ```
@@
 Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
-```{r business, echo = FALSE, fig.align = "center"}
+```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
+ggplot(ratings_business,aes(x=stars, y=count)) +  
+  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
+  scale_y_continuous(limits=c(300,5000)) +
+  xlab("Star Ratings") + 
+  ylab("Review Counts") +
+  theme(text = element_text(family = "Times New Roman"))
+
 ggplot(successful_business, aes(x = reorder(state, -num), 
@@
   group_by(word) %>% 
-  count() %>% 
+  tally() %>% 
   top_n(100) %>% 

### 2016-08-09 rscripts/business.R

@@ -1,73 +1,0 @@
-library(readr)
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(magrittr)
-library(ggmap)
-library(maps)
-library(jsonlite)
-
-business <- fromJSON(sprintf("[%s]", 
-                             paste(readLines("yelp_academic_dataset_business.json"), 
-                                   collapse = ","))) %>% 
-  flatten() %>% 
-  select(open, categories, review_count, state, stars, `attributes.Noise Level`, `attributes.Attire`, `attributes.Take-out`, `attributes.Takes Reservations` `attributes.Delivery`, `attributes.Outdoor Seating`, `attributes.Accepts Credit Cards`,`attributes.Happy Hour`) %>% 
-  # should filter for restaurants 
-  filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
-names(business) <- c("open", "categories", "count", "long", "lat", "state", "stars", "noise", "attire")
-states <- map_data('state')
-# Show data from all over US
-us_business <- filter(business, count > 300)
-ggplot(states) + 
-  geom_polygon(aes(x = long, 
-                   y = lat, 
-                   group = group), 
-               fill = "grey80", 
-               color = "white") + 
-  coord_fixed(1.3) + 
-  geom_point(data = us_business, 
-             aes(long, 
-                 lat, 
-                 color = factor(stars), 
-                 size = count), 
-             alpha = 0.7) + 
-  guides(colour = guide_legend("Star Rating"), 
-         size = guide_legend("Review Counts")) + 
-  labs(title = "Restaurant Reviews in United States") +
-  theme_nothing(legend = TRUE)
-# Show number of businesses in each state (popularity) 
-top_data <- us_business %>% 
-  group_by(state) %>% 
-  tally()
-
-big_cities <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA")
-# Focusing on attribute noise level
-noise_data <- big_cities %>% 
-  group_by(state, noise) %>% 
-  summarise(star = mean(stars)) 
-noise_data$noise_factored <- factor(noise_data$noise, 
-                                labels=c("quiet",
-                                         "average",
-                                         "loud", 
-                                         "very_loud"))  
[…]

### 2016-08-09 rscripts/irene-cleandata.R

@@ -1,84 +1,0 @@
-business <- fromJSON(sprintf("[%s]", 
-                             paste(read_lines("yelp_academic_dataset_business.json"), 
-                                   collapse = ","))) %>% 
-  flatten() %>% 
-  select(open, categories, review_count, longitude, 
-         latitude, state, stars, latitude, `attributes.Noise Level`, 
-         `attributes.Attire`) %>% 
-  # should filter for restaurants 
-  filter(open == TRUE, "Restaurants" %in% categories, state %in% state.abb)
-names(business) <- c("open", "categories", "count", "long", 
-                     "lat", "state", "stars", "noise", "attire")
-
-# Business data with review counts exceeding 300.
-us_business <- filter(business, count > 300) 
-us_business <- data.frame(lapply(us_business, as.character), 
-                          stringsAsFactors=FALSE)
-write_csv(subset(us_business), "us-business.csv")
-
-# Data: Star ratings with noise level attribute
-noise_level <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
-  group_by(state, noise) %>% 
-  summarise(star = mean(stars)) 
-noise_level$noise_factored <- factor(noise_level$noise, 
-                                     labels=c("quiet",
-                                              "average",
-                                              "loud", 
-                                              "very_loud"))  
-write_csv(subset(noise_level), "noise-attr.csv")
-
-# Data: Star ratings with attire type attribute
-attire_type <- business %>% 
-  na.omit() %>% 
-  filter(state == "NV" | state == "AZ" | state == "NC" | state == "PA") %>% 
-  group_by(state, attire) %>% 
-  summarise(star = mean(stars))
-write.csv(subset(attire_type), "attire-attr.csv")
-
-# Data: 
-review <- fromJSON(sprintf("[%s]", 
-                           paste(read_lines("yelp_academic_dataset_review.json", 
-                                            n_max = 1500000), 
-                                 collapse = ","))) %>% 
-  select(user_id, review_id, stars, business_id)
-
-
-user <- fromJSON(sprintf("[%s]", 
-                         paste(read_lines("yelp_academic_dataset_user.json",
-                                          n_max = 100000), 
-                               collapse = ",")))
-
-business_location <- fromJSON(sprintf("[%s]", 
[…]

### 2016-08-09 clean_data/CleanData.R
cleaning

@@ -42,3 +42,44 @@ users <- data.frame(lapply(users, as.character), stringsAsFactors=FALSE)
 write_csv(business, "yelp_business.csv")
 write_csv(reviews, "yelp_reviews.csv")
 write_csv(users, "yelp_users.csv")
+
+# ------------------- Mutating Data for Sentiment Graphs Below -----------------------
+review_sample <- read_csv("yelp_reviews.csv") %>% 
+  sample_n(500000)
+reviews_text <- review_sample %>% 
+  select(business_id, review_id, stars, text) %>%
+  unnest_tokens(word, text) %>% 
+  anti_join(stop_words) %>% 
+  arrange(review_id)
+
+write_csv(reviews_text, "reviews_text.csv")
+
+# rank words from -5 (negativity) to 5 (positivity) using AFINN lexicon
+# sentiments: 
+#   data frame with 4 variables: word, sentiment, lexicon, score
+# lexicon can be "nrc", "bing", or "AFINN"
+valence_score <- sentiments %>% 
+  filter(lexicon == "AFINN") %>% 
+  select(word, score)
+
+# calculate mean for each review
+# Tidied: review_id, star rating, average sentiment score
+review_scores <- reviews_text %>% 
+  inner_join(valence_score, by = "word") %>% 
+  group_by(review_id, stars) %>% 
+  summarise(sentiment = mean(score))
+write_csv(review_scores, "review_scores.csv")
+
+review_words <- reviews_text %>% 
+  count(review_id, business_id, stars, word) %>% 
+  ungroup()
+summaries <- review_words %>% 
+  group_by(word) %>% 
+  summarise(business = n_distinct(business_id),
+            reviews = n(),
+            average_star = mean(stars)) %>% 
+  ungroup() %>% 
+  filter(reviews >= 500, business >= 10) %>% 
+  inner_join(valence_score, by = "word")
+head(summaries, n = 10)
+write_csv(summaries, "summaries.csv")

### 2016-08-09 paper/paper.Rmd
abstract

@@
 ---
-title: "Final Paper"
+title: "Yelp Academic Dataset Final Report"
+author: Anuj Desai & Irene Lee
 output: pdf_document
@@
 library(magrittr)
-library(ggmap)
 library(tidytext)
@@
 ```
+
+## Abstract
+
+This paper explores the deep dataset of Round 7 of the Yelp Academic Dataset challenge.
+With three primary foci, we wanted to analyze the relationship between business attributes and rating, to use sentiment analysis tools to determine the correlation between text in Yelp reviews and the business's rating, and finally to analyze user behavior in unfamiliar locations when reviewers travel.
+Our findings revealed that while there was no significant evidence of any relationship between business attributes and rating and travel and user rating, there was strong evidence that suggested that review text could predict star rating.
 
@@
 business <- read_csv("../clean_data/yelp_business.csv")
-names(business) <- c("business_id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")
+names(business) <- c("business_id", "open", "categories", "count", "state",
+                     "stars", "noise", "attire", "Take-out", 
+                     "Takes Reservation", "Offers Delivery", "Outdoor Seating",
+                     "Accepts Credit Card", "Happy Hour")
 successful_business <- business %>% 
@@
 Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
-```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
-ggplot(ratings_business,aes(x=stars, y=count)) +  
-  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
-  scale_y_continuous(limits=c(300,5000)) +
+```{r business, echo = F, fig.align = "center", message = F, fig.height = 3.5}
+ggplot(ratings_business, aes(x = stars, y = count)) +  
+  geom_point(col = rgb(0, 0, 1, 0.25), pch = 16, cex = 2) +
+  scale_y_continuous(limits = c(300, 5000)) +
   xlab("Star Ratings") + 
@@
 ggplot(successful_business, aes(x = reorder(state, -num), 
-                                y= num)) + 
+                                y = num)) + 
   geom_bar(stat = "identity", 
@@
 We hypothesized that words with higher valence scores would produce higher Yelp star ratings for businesses.
-First, using the R library “wordcloud”, we formed two word clouds for the 100 most frequent words in text reviews with one-star and five-star ratings to determine if there was a distinct difference between the words used.
+First, using the R library “__wordcloud__”, we formed two word clouds for the 100 most frequent words in text reviews with one-star and five-star ratings to determine if there was a distinct difference between the words used.
 
@@
                color = NA) +
-  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
   xlab("Average Star Ratings") + 
@@
                     values = c("blue", "red"),
-                    labels = c("Familiar", "Unfamiliar"))
+                    labels = c("Familiar", "Unfamiliar")) +
+  theme(text = element_text(family = "Times New Roman"))
 ```
@@
 ##Conclusion
-In conclusion, we investigated several questions related to the Yelp datasets, and our results were promising.
+In conclusion, we investigated several questions related to the Yelp academic dataset, and our results were promising.
 

### 2016-08-09 paper/paper.Rmd
paper updated'

--- 2016-08-09 paper/paper.Rmd
@@
 
-Our first hypothesis was that successful businesses would be clustered at certain points.
+Our first hypothesis was that successful businesses would be clustered at certain states.
+We examined the data set and wanted to know about the relationship between the number of reviews and the star ratings.
+It turned out that when number of reviews increases, the star ratings gets clustered around 3.5 out of 5.
+Hence, we hypothesized that high number of reviews, especially those locations with most reviewed businesses, will have positive influence to the star ratings.
+
 We first tried to plot this information with points on a map using longitude and latitude of the businesses.
@@
 Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
-```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
+```{r business, echo = FALSE, fig.align = "center", message = FALSE, fig.height = 3.5, warning = FALSE}
 ggplot(ratings_business,aes(x=stars, y=count)) +  
@@
 Our findings pointed out that business attributes do not have huge influences over user ratings.
-```{r attributes, echo = FALSE, fig.align = "center"}
+```{r attributes, echo = FALSE, fig.align = "center", message = FALSE}
 business_attributes <- business %>% 
@@
 
-```{r density, echo = FALSE, fig.align = "center"}
+```{r density, echo = FALSE, fig.align = "center", message = FALSE}
 selected_users <- users %>% 
@@
 
+There is a close relationship between star ratings and number of reviews--the popularity of the business.
+There are certain locations where most reviewed businesses are clustered; hence, location also has some influence over the star ratings.
+However, no significant correlations between business attributes and the review ratings were found.
+
 Using natural language processing and text mining, we confirmed our original hypothesis that a positive correlation exists between AFINN sentiment score and star rating.
 86.59% of words with negative scores appeared in reviews that were below the mean rating of all reviews from our sample.
+
+Lastly, by examining the behavior of users while travelling showed that most users tend to give mediocre ratings when in unfamiliar places.
+On the other hand, the ratings were evenly distributed while in familiar locations.
+Surprisingly the mean of each situation was about the same.
 
@@
 Additionally, we could look at possible correlations between restaurant reviews and ratings and tips, looking at the tips data provided with the dataset.
+
+At last, we could use full data set instead of an academic, truncated data provided for data challenge.
+This way we could utilize more information to make even accurate plots and analysis.
+Using this, a comparison of user trends in different countries will be interesting for further investigation.

### 2016-08-09 paper/paper.Rmd

--- 2016-08-09 paper/paper.Rmd
@@
 Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona.
-```{r business, echo = F, fig.align = "center", message = F, fig.height = 3.5}
-ggplot(ratings_business, aes(x = stars, y = count)) +  
-  geom_point(col = rgb(0, 0, 1, 0.25), pch = 16, cex = 2) +
-  scale_y_continuous(limits = c(300, 5000)) +
+
+```{r business, echo = FALSE, fig.align = "center", message = FALSE, fig.height = 3.5, warning = FALSE}
+ggplot(ratings_business,aes(x=stars, y=count)) +  
+  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
+  scale_y_continuous(limits=c(300,5000)) +
   xlab("Star Ratings") + 
@@
 ##Conclusion
-In conclusion, we investigated several questions related to the Yelp academic dataset, and our results were promising.
+
+In conclusion, we investigated several questions related to the Yelp datasets, and our results were promising.
+
+There is a close relationship between star ratings and number of reviews--the popularity of the business.
+There are certain locations where most reviewed businesses are clustered; hence, location also has some influence over the star ratings.
+However, no significant correlations between business attributes and the review ratings were found.
 
@@
 86.59% of words with negative scores appeared in reviews that were below the mean rating of all reviews from our sample.
+
+Lastly, by examining the behavior of users while travelling showed that most users tend to give mediocre ratings when in unfamiliar places.
+On the other hand, the ratings were evenly distributed while in familiar locations.
+Surprisingly the mean of each situation was about the same.
 

### 2016-08-09 eda/sentiment-analysis.Rmd
notes

@@
 library(tm)
+library(ggrepel)
 library(purrr)
@@
 # boxplot for each group
+# ggplot(review_scores, aes(star, sentiment)) +
+#   geom_bar(stat = "identity")
+# coloring too messy, histogram/bar graph doesn't capture whole picture
+# want to see if some 1-star ratings have 5s and vice versa
+# boxplot shows this with outliers
 ggplot(review_scores) +
@@
 ```{r fig.height = 7, fig.width = 7}
+# x scale log - graph messy otherwise
+# ggrepel - too much text, unreadable 
+# line color black and dotted = most visible
+# color scheme most visible
+# plot less points? not meaningful enough then
 summaries %>% 
@@
 ```{r fig.height = 7}
+# boxplot again?
+# see specific words and overall trend
+# line doesn't fit that well but shows positive trend so best fit
 summaries %>% 
@@
   geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
-  geom_smooth(method = "lm", se = FALSE) +
+  geom_smooth(method = "loess", se = FALSE) +
   xlab("Valence Score") +
@@
 ```{r}
+# histogram complains
+# bar graph good (Y)
 data.frame(

### 2016-08-09 eda/sentiment-analysis.Rmd
loess vs line

@@
 # see specific words and overall trend
-# line doesn't fit that well but shows positive trend so best fit
+# line best fit - shows general trend
+# loess not good fit
 summaries %>% 
@@
   geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
-  geom_smooth(method = "loess", se = FALSE) +
+  geom_smooth(method = "lm", se = FALSE) +
   xlab("Valence Score") +

### 2016-08-09 paper/paper.Rmd
jitter

@@
 
-```{r business, echo = FALSE, fig.align = "center", message = FALSE, fig.height = 3.5, warning = FALSE}
-ggplot(ratings_business,aes(x=stars, y=count)) +  
-  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
-  scale_y_continuous(limits=c(300,5000)) +
+```{r business, echo = F, fig.align = "center", message = F, fig.height = 3.5, warning = F}
+ggplot(ratings_business, aes(x = stars, y = count)) +  
+  geom_jitter(col = rgb(0, 0, 1, 0.25), pch = 16, cex = 2, width = 0.25) +
+  scale_y_continuous(limits = c(300, 5000)) +
   xlab("Star Ratings") + 

### 2016-08-09 paper/paper.Rmd
data changed little

--- 2016-08-09 paper/paper.Rmd
@@
 users <- read_csv("../clean_data/yelp_users.csv")
-reviews <- read_csv("../clean_data/yelp_reviews.csv")
 ```

### 2016-08-09 paper/paper.Rmd
final version updated

@@
 
-The mean rating was 3.718 for unfamiliar and 3.762 for familiar places.
-However, the standard deviation for the familiar locations plot was 0.41, and unfamiliar one was 1.37 so star rating, explained by the variablity between users who travelled.
+However, it was interesting to see that the mean rating was 3.718 for unfamiliar and 3.762 for familiar places.
+They were almost equal to each other despite of such user's behavioral changes on familiarity with the location.
 
